---
title: "Data wrangling for ATT - VEMCO data edit"
author: "Ben Cresswell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
 html_document:
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 4
    fig_width: 4
    highlight: textmate
    theme: spacelab
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: inline
---


This Rmd takes the output of the diw.Rmd (alldata), along with tag/receiver metadata, and converts into a format suitable for making an ATT object

# PRELIMINARIES #

# Set up Rmd
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
```

# Load required packages
```{r packages, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(writexl)
library(VTrack)
library(readxl)
library(arsenal) # For comparing differences in tibbles 
library(lubridate)
library(tidyverse)
```


# Step 1. Main detection data set up


# Load detection data
```{r}
load(file = "../data/RData/alldata.RData")
```

## Check against format required for IMOS/ATT:
```{r}
data(IMOSdata) # Note: the VEMCOdata file format that comes with vTrack would be a better format for us (more similar to our raw data), however the ATT code/fxns doesn't work on it!!
```

## And compare (run whole chunk at once)
```{r}
glimpse(alldata)
glimpse(IMOSdata)
```

Missing some columns and others have different names and some are also wrong format (IMOS data has dttm as factor) 

## Convert to ATT format:
```{r}
setupdata <- alldata %>% 
  mutate(tag_id	= transmitter_id,
         transmitter_id = transmitter_id,
         FID = factor(NA),
         id =	NA, 
         file_id = NA,
         url = factor(NA),
         release_id = Project_code,
         tag_project_name	= factor('CSMP'),
         common_name = Common_name,
         scientific_name = Scientific_name,
         installation_name = NA,
         station_name =	station_name,
         receiver_name = receiver_name,
         detection_timestamp = detection_timestamp,
         longitude = Long,
         latitude =	Lat,
         sensor_value =	Sensor.Value,
         sensor_unit = factor(NA),
         FDA_QC	= NA,
         Velocity_QC = NA,
         Distance_QC = NA,
         DetectionDistribution_QC =	NA,
         DistanceRelease_QC =	NA,
         ReleaseDate_QC =	NA,
         ReleaseLocation_QC =	NA,
         Detection_QC	= NA,
         release_longitude = Long,
         release_latitude	= Lat,
         ReleaseDate = Date,
         sensor_slope = Slope,
         sensor_intercept = Intercept,
         sensor_type = Type,
         tag_sensor_unit = NA,
         tag_model_name = Model,
         tag_serial_number = Serial,
         tag_expected_life_time_days = NA,
         tag_status = NA,	
         sex = Sex,
         measurement = TL,
         dual_sensor_tag = NA,
         geom	= NA,
         .keep='none')

summary(setupdata$sensor_intercept)
summary(alldata$Intercept)

```

## And check against IMOSdata (run whole chunk at same time)
```{r}
# General overview 
#glimpse(setupdata)
#glimpse(IMOSdata)

# List of column names
#print(tibble(colnames(setupdata)), n=100)
#print(tibble(colnames(IMOSdata)), n=100)
# (Here you can copy out the lists of column names into csv for an external)
```

## Formal check using arsenal
```{r}
#cols1 <- tibble(colnames(setupdata))
#cols2 <- tibble(colnames(IMOSdata))
#summary(comparedf(cols1, cols2))
```

Looks good = save
```{r}
save(setupdata, file = "../data/RData/ATTsetupdata.RData")
```


# Step 2. Tag metadata

## Load the list of known tags deployed in QLD/GBR/CSMP region
The following chunk runs a separate script to import files relating to both sharks and teleosts tagged in the regions (From Adam's master list) and combines to make one database of tagged animals ("regional_tag_list):
```{r warning=FALSE}
source("../code/regional_tag_list.R", local = knitr::knit_global())
rm("regional_shark_list", "regional_teleost_list") # Remove the individual shark and telost lists as we don't need them separately (for now)
```

## From this list we'll extract all the known regional tags that are in our detection database
```{r}
ATTdetected_tags <- setupdata %>% 
  distinct(transmitter_id) %>% 
  merge(regional_tag_list)
```

## Save as RData
```{r}
save(ATTdetected_tags, file = "../data/RData/detected_tags.RData")
```


## Create tag metadata (IMOS ATT format)
```{r} 
tagdata <- detected_tags %>% 
  mutate(tag_id = transmitter_id,
         transmitter_id = transmitter_id,
         release_id = Project_code,
         tag_project_name = 'CSMP',
         scientific_name = Scientific_name,
         common_name = Common_name,
         embargo_date = NA,
         is_protected = FALSE,
         release_longitude = Long,
         release_latitude = Lat,
         ReleaseDate = factor(Date),
         sensor_slope = as.numeric(Slope),
         sensor_intercept = as.numeric(Intercept),
         sensor_type = Type,
         sensor_unit = factor(case_when(grepl("press", `Type`) ~ "Meters",      
                                 grepl("temp", `Type`) ~ "Celcius")),
         tag_model_name = Model,
         tag_serial_number = as.integer(Serial),
         tag_expected_life_time_days = as.integer(NA),
         tag_status = factor('DEPLOYED'),
         sex = Sex,
         measurement = factor(TL),
         dual_sensor_tag = FALSE,
         .keep='unused')
```

## And compare against the IMOS format
```{r}
data("taginfo")
glimpse(tagdata)
glimpse(taginfo)

```


# Step 3. Receiver (station) metadata
```{r}
# File per deployment
vr2ws_dep1 <- read_excel('../data/receiver_list_dep1.xlsx', trim_ws = TRUE)
vr2ws_dep2 <- read_excel('../data/receiver_list_dep2.xlsx', trim_ws = TRUE)
# And join
stationdata <- rbind(vr2ws_dep1, vr2ws_dep2) %>% 
  mutate(status='DEPLOYED',    # Add some extra columns on that should be there
         imos_device='FALSE')
```


## Compare against IMOS format

```{r}
data("statinfo")
glimpse(stationdata)
glimpse(statinfo)

```



# Step 4

# Now try to make an ATT object
```{r eval=TRUE, message=FALSE, warning=FALSE}
myATTdata <- setupData(Tag.Detections = setupdata, 
                     Tag.Metadata = tagdata, 
                     Station.Information = stationdata, 
                     source = "IMOS")
```

## Load IMOSdata for comparison
```{r eval=TRUE, message=FALSE, warning=FALSE}
data("IMOSdata")
ATTdata <- setupData(Tag.Detections = IMOSdata, 
                     Tag.Metadata = taginfo, 
                     Station.Information = statinfo, 
                     source = "IMOS")
```

## Compare
```{r}
## Can't compare whole objects easily (as they are lists) but can check sub-units of what's in there:
glimpse(ATTdata$Tag.Detections)
glimpse(myATTdata$Tag.Detections)
```
Looks good so we'll save!


```{r}
save(myATTdata, file = "../data/RData/myATTdata.RData")
```




