---
title: "Investigating data using ATT"
author: "Ben Cresswell"
date: "31/03/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Load ATT data for our project
```{r}
load(file = "../data/RData/myATTdata.RData")
```

# EDA

## Braod overview
```{r}
myATTdata$Tag.Detections
```


## Calculating detection metrics

## Detection summary (won't work if setup not correct)
```{r, eval=TRUE, message=FALSE, warning=FALSE}
## Calculate detecion metrics with monthly subsets chosen
detSum <- detectionSummary(myATTdata,  
                           sub = "%Y-%m") # Nico mentioned a potential issue with this - if you've tagged an individual halfway throguh the month, will it show up?
```


`detectionSummary()` outputs a list object with two components, `$Overall`: detection metrics for the full period of the tag and `$Subsetted`: detection metrics for weekly or monthly temporal subsets depending on the `sub` argument. 

# Assign the detection summary components to stand-alone tibbles
```{r, eval=FALSE}
## Accessing metrics of detection for full tag life
totaldets <- tibble(detSum$Overall) %>% 
  mutate_if(is.character, as.factor)
## Accessing metrics of detection for each temporal subset
subsetdets <- tibble(detSum$Subsetted) %>% 
    mutate_if(is.character, as.factor)

```

Can use these to filter out individuals or species

```{r}
gtdets <- totaldets %>% 
  filter(Sci.Name == 'Caranx ignobilis')
gtdets

```






#### EXPERIMENT ####

Can we subset inside an ATT object?

```{r}





```





## Create an abacus plot
```{r, eval=FALSE}
abplot <- abacusPlot(ATTdata = myATTdata) # Pointlessly large (all transmitters and all receivers) - need to filter data down a bit
#abplot
#ggsave(abplot, filename = "../output/abplottest.png")
```

# Facetted abacus plot
```{r facet-abacus, eval=FALSE, message=FALSE, warning=FALSE}
## Create a facetted abacus plot for groups
## Silvertips
silvers <- abacusPlot(ATTdata = myATTdata, 
           id = c("A69-9001-60566","A69-9001-60571", "A69-9001-64072"), # Can add more
           facet = TRUE)

tigers <-  abacusPlot(ATTdata = myATTdata, 
           id = c("A69-9001-4172","A69-9001-63847", "A69-9001-63947"), # Can add more
           facet = TRUE)
tigers
ggsave(tigers, filename = "../output/gcuvier_detections.png")
```



```{r}

osprey_grs_list <- detected_tags %>% 
  mutate(across(where(is.factor), as.character)) %>% 
  filter(Location == 'Osprey') %>% 
  filter(Common_name == 'Grey Reef') %>% 
  pull(Tag_ID)

```


```{r}

os_grs_ab <- abacusPlot(ATTdata = myATTdata, 
           id = osprey_grs_list, # Can add more
           facet = TRUE)

os_grs_ab
ggsave(os_grs_ab, filename = "../output/os_grs_abacus.png", width=16,  height=10, dpi = 1000)


```



# Calculate center of activity (COA) 

```{r coa-calc, eval=TRUE, message=FALSE, warning=FALSE}
myCOAdata <- COA(ATTdata = myATTdata, 
               timestep = 60, ## timestep bin used to estimate centers of activity (in minutes)
               split = TRUE)
```

`COA()` produces a single tibble data frame with centers of activity positions estimated for each timestep bin when `split = FALSE`; and a list object with centers of activity positions for each individual when `split = TRUE`.


## Check
```{r, coa-check1, eval=TRUE, message=FALSE, warning=FALSE}
myCOAdata[1:2] # THis just gives you the first 2 Tag IDs
```


## Can view by specific fish
```{r, eval=TRUE, message=FALSE, warning=FALSE}
COAdata$`77523307`
```

# Now can calculate activity space metrics

## First define projected Coordinate Reference System 
```{r}
# Projected coordinate systems should signify distance in meters so the output area values are in sq meters
# (here epsg:3577 refers to the GDA94 Australian Albers projection)
proj <- sp::CRS("+init=epsg:3577")
```


## Estimate 100% Maximum Convex Polygon (MCP) areas
```{r warning=FALSE}
mymcp_est <- HRSummary(COAdata = myCOAdata, 
                     projCRS = proj, 
                     type = "MCP", 
                     cont = 100,
                     sub = "%Y-%m")
mymcp_est
```



```{r, eval=FALSE, message=FALSE, warning=FALSE}
##*** Warning: the following might take a little while to run! ***##
## Estimate 50% and 95% fixed Kernel Utilisation Distribution ('fKUD') contour areas with cumulative metrics calculated
myfkud_est <- HRSummary(COAdata = myCOAdata, 
                      projCRS = proj, 
                      type = "fKUD",
                      cont = c(50,95),
                      cumulative = TRUE)  
```

## Storing spatial data associated with activity space metrics

MCP polygons and probability distributions associated with fKUD and BBKUDs can be stored when `storepoly = TRUE`. This outputs a list object with the two components, `$Overall`: a tibble data frame with activity space metrics for the full period of the tag and `$Subsetted`: a tibble data frame with activity space metrics for weekly or monthly temporal subsets depending on the `sub` argument, but also includes an additional `$Spatial.Objects` list that stores polygons (if calculating MCPs) or probability distribution raster (if calculating fKUD or BBKUD) for full tag life and temporal subsets.

```{r, echo=TRUE, results='hide', fig.keep='all', message = FALSE, warning=FALSE}
## Estimate 20%, 50% and 95% Brownian Bridge Kernel Utilisation Distribution ('BBKUD') contour areas and store polygons
myBBkud_est <- HRSummary(COAdata = myCOAdata, 
                       projCRS = proj, 
                       type = "BBKUD", 
                       cont = c(20,50,95), 
                       storepoly = TRUE)
```

## Map activity space

```{r, eval=TRUE, message=FALSE, warning=FALSE}
## Base plots using raster
# Activity space for full tag life
library(tidyverse)
library(lubridate)
library(raster)
library(viridis) ## access more color palettes!
## Select rasters of full KUDs for each individual into a single list
fullstack <-
  unlist(BBkud_est$Spatial.Objects)[grep("*_full", names(unlist(BBkud_est$Spatial.Objects)))]
names(fullstack) <-
  unlist(lapply(strsplit(names(fullstack), "[.]"), `[[`, 1))

## Lets plot the overall BBKUD for Tag.ID `A69-1602-50959`
fulltag <- fullstack$`A69-1602-50959`

fulltag

#values(fulltag)[values(fulltag) > 96] <- NA
raster::plot(fulltag, col = viridis(100), zlim = c(0, 100),
     xlim=c(146.53, 146.59), ylim=c(-13.92, -13.85))
points(station_latitude ~ station_longitude, statinfo, col = 2, cex=0.7)
points(Latitude.coa ~ Longitude.coa,
       data = myCOAdata$`A69-1602-50959`,
       pch = 20,
       col = 4,
       cex = 0.5)
contour(fulltag, add = TRUE, levels = c(50, 95))
```













































