---
title: "Data analysis and visualisation - grey reef sharks"
author: "Ben Cresswell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
 html_document:
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 4
    fig_width: 4
    highlight: textmate
    theme: spacelab
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: inline
---


# Set up Rmd
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#rm(list=ls())
```

# Load required packages
```{r packages, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(writexl)
library(readxl)
library(lubridate)
library(magrittr)
library(tidyverse)
#library(VTrack) # Current R version doesn't like VTrack - may need to install an earlier version..
```

# Load data

```{r}
load(file = "data/RData/alldata.RData")

# Direct from wrangling folder
load("../CSMPWrangling/data/RData/alldata.RData")
```

```{r}
# All greys
grs_all <- 
  alldata %>% 
  filter(Common_name == 'Grey Reef')

```


## Check 
```{r}
glimpse(grs_all)
summary(grs_all$Location)
```
# Filter out by location
```{r}
# Greys tagged at Osprey Reef
os_grs <- alldata %>% 
  filter(installation_name == 'Osprey') %>% 
  filter(Common_name == 'Grey Reef')

# Greys tagged at Bougainville Reef - 0
br_grs <- alldata %>% 
  filter(installation_name == 'Bougainville') %>% 
  filter(Common_name == 'Grey Reef')

# Greys tagged at Holmes Reef
hr_grs <- alldata %>% 
  filter(installation_name == 'Holmes') %>% 
  filter(Common_name == 'Grey Reef')

# Greys tagged at Flinders Reef
fr_grs <- alldata %>% 
  filter(installation_name == 'Flinders') %>% 
  filter(Common_name == 'Grey Reef')
```


# Large scale movements - do any individuals move between entire reef sites?

##  Will explore using abacus plot, faceted out by installation name (of where receiver was)
```{r fig.height = 100/25.4, fig.width = 160/25.4}
grs_ab_main <- 
grs_all %>%
  ggplot(mapping = aes(x = detection_timestamp, y = installation_name)) + 
  xlab("Date") + 
  ylab("Tag") +
  geom_point() +
  facet_wrap(~ Serial)
grs_ab_main
```

## Save to get a better look
```{r save-silver-ab}
ggsave(filename = '../output/greys_abacus_overview.png', grs_ab_main , width = 600, height = 200, units = 'mm', dpi = 300)
```

A69-9001-60580 moved from Flinders to Holmes in late November:
```{r}
grs_all %>%
  filter(transmitter_id == "A69-9001-60580") %>% 
  ggplot(mapping = aes(x = detection_timestamp, y = site_code)) + 
  xlab("Date") + 
  ylab("Tag") +
  geom_point()
```

# What about movements a smaller scale? Say between N and S Flinders or E and W Holmes? Or between Osprey wall and lagoon?

## Osprey - by station
```{r fig.height = 100/25.4, fig.width = 160/25.4}
# Whole cohort
os_grs %>%
  ggplot(mapping = aes(x = detection_timestamp, y = station_name_long)) + 
  xlab("Date") + 
  ylab("Tag") +
  geom_point() +
  facet_wrap(~ transmitter_id)

# TP only
os_grs %>%
  filter(Type != "pinger") %>% 
  ggplot(mapping = aes(x = detection_timestamp, y = station_name_long)) + 
  xlab("Date") + 
  ylab("Tag") +
  geom_point() +
  facet_wrap(~ transmitter_id)
```


## Osprey - whole installation

# If you want one row per T/P animal you need to combine their separate temp and press logs:

```{r}
# All grey reef shark sensor data
grs_sensor_data <- 
  grs_all %>% 
  filter(!is.na(Sensor.Value)) %>% 
  filter(!is.na(Type)) %>% 
  droplevels()

# Osprey only sensor data
osp_grs_sensor_data <- 
  grs_sensor_data %>% 
  filter(installation_name == 'Osprey')

# All grey reef shark non-sensor data
grs_non_sensor_data <- 
  grs_all %>% 
  filter(Type == "pinger") %>% 
  droplevels()

# Osprey only non-sensor data
osp_grs_nonsensor_data <- 
  grs_non_sensor_data %>% 
  filter(installation_name == 'Osprey')

```



## Assign just one transmitter id to each sensor tag

Currently each animal has 2 x transmitter IDs for their tag - one for temp and one for pressure. If we want to to look at individual animal patterns we'll need to combine these. First will need to check which transmitter IDs go together, based on the serial number (which is the same for both T and P components):
```{r}
osp_grs_sensor_data %>% 
  dplyr:: select(transmitter_id, Serial, Org_type, Type) %>% 
  distinct() %>% 
  arrange(transmitter_id)
```


Lower-even ID for temp goes with a higher-odd ID for press: Need to +1 to every temp/even ID

We'll do this and at the same time will calibrate using the calibration coefficients (slope and intercept) for the tags as provided by Vemco.

Calibration coefficients:

    Slope	    Intercept
P   0.9097	  -3.6388
T   0.1575	  -5.157

# Calculate temp
```{r}
osp_grs_temp_data <- 
  osp_grs_sensor_data %>%
  filter(Org_type == "Elasmobranch") %>% 
  filter(ID %% 2 != 1)  %>% 
  #dplyr::select(transmitter_id) %>% 
  mutate(ID = ID+1) %>% 
  mutate(transmitter_id = factor(paste(Freq, Space, ID, sep = '-'))) %>% 
  mutate(Temp = `Sensor.Value` * Slope + Intercept)

```

# Calculate depth 
```{r}
osp_grs_press_data <- 
  osp_grs_sensor_data %>%
  filter(Org_type == "Elasmobranch") %>% 
  filter(Type =="press") %>% 
  mutate(Depth = `Sensor.Value` * Slope + Intercept) %>% 
  mutate(Depth = if_else(Depth <0, 0, Depth)) # Have a few negative values (up to c. -3) - clearly cannot be out of the water so will reset to 0
```

# Combine together so that temp and depth in the same dataframes
```{r}
osp_grs_tp_data <- 
  osp_grs_temp_data %>% 
  full_join(osp_grs_press_data) %>% 
  #dplyr::select(transmitter_id, detection_timestamp, station_name, station_name_long, Scientific_name, Date_tagged, 
   #      Location_tagged, Site_tagged, Sex, FL, TL, Lat, Long, Temp, Depth) %>% 
  #filter(!grepl("Lagoon", station_name_long),        # just a few shark detections (2 individs 14041 and 14059) from lagoon1 so filtering out
#         station_name_long != "Overnight_Mooring"   # may need to leave ONM out as it only has shallow detections but will leave in for now
       # ) %>%  
 # filter(detection_timestamp < as.Date("2022-11-01 00:00:01")) %>% 
  arrange(detection_timestamp) %>% 
  droplevels()
```

# Combine sensor and non-sensor data (Osprey only here)
```{r}
os_grs2 <- 
  osp_grs_tp_data %>% 
  full_join(osp_grs_nonsensor_data)

```


```{r fig.height = 100/25.4, fig.width = 160/25.4}

os_grs2 %>%
  dplyr::select(transmitter_id, Sex) %>% 
  unique() %>% 
  group_by(transmitter_id)  %$% 
  summary(Sex)
  


os_grs_tp_abacus <- 
os_grs2 %>%
  filter(Type != "pinger") %>% 
  filter(detection_timestamp > as.Date("2021-10-30 00:00:00")) %>% 
  filter(detection_timestamp < as.Date("2022-10-30 00:00:00")) %>% 
  ggplot(mapping = aes(x = detection_timestamp, y = transmitter_id)) + 
  xlab("Date") + 
  ylab("Tag") +
  geom_point() +
  theme_light()

os_grs_pinger_abacus <- 
os_grs2 %>%
  filter(Type == "pinger") %>% 
  #filter(detection_timestamp > as.Date("2021-10-30 00:00:00")) %>% 
  #filter(detection_timestamp < as.Date("2022-10-30 00:00:00")) %>% 
  ggplot(mapping = aes(x = as.Date(detection_timestamp), y = as.character(transmitter_id))) + 
  #annotate("text", x = as.Date("2021-10-30 00:00:00"), y = 2, lab = "blah") + # Boxes to indicate depth movement study period
  geom_vline(xintercept = as.Date("2021-10-30 00:00:00"), colour = "blue", linewidth = 2) +
  geom_vline(xintercept = as.Date("2022-10-30 00:00:00"), colour = "blue", linewidth = 2) +
  xlab("Date") + 
  ylab("Tag") +
  geom_point() +
  theme_minimal()

os_grs_tp_abacus
os_grs_pinger_abacus

#os_grs_installation_abacus

getwd()

ggsave(filename = "output/os_grs_tp_abacus.jpg", os_grs_tp_abacus , width = 160, height = 100, units = 'mm', dpi = 300)
ggsave(filename = "output/os_grs_pinger_abacus.jpg", os_grs_pinger_abacus , width = 160, height = 100, units = 'mm', dpi = 300)
```



# Bougainville cohort
```{r fig.height = 10, fig.width = 16}
br_grs %>%
  ggplot(mapping = aes(x = detection_timestamp, y = installation_name)) + 
  xlab("Date") + 
  ylab("Tag") +
  geom_point() +
  facet_wrap(~ transmitter_id)
```

# Holmes cohort
```{r fig.height = 10, fig.width = 16}
hr_grs %>%
  ggplot(mapping = aes(x = detection_timestamp, y = station_name)) + 
  xlab("Date") + 
  ylab("Tag") +
  geom_point() +
  facet_wrap(~ transmitter_id)
```

 
# Flinders cohort
```{r fig.height = 10, fig.width = 16}
fr_grs %>%
  ggplot(mapping = aes(x = detection_timestamp, y = installation_name)) + 
  xlab("Date") + 
  ylab("Tag") +
  geom_point() +
  facet_wrap(~ transmitter_id)
```

 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 











