---
title: "Data analysis and visualisation - grey reef sharks"
author: "Ben Cresswell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
 html_document:
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 4
    fig_width: 4
    highlight: textmate
    theme: spacelab
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: inline
---


# Set up Rmd
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#rm(list=ls())
```

# Load required packages
```{r packages, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(writexl)
library(readxl)
library(lubridate)
library(tidyverse)
#library(VTrack) # Current R version doesn't like VTrack - may need to install an earlier version..
```

# Load data
```{r}
# All greys
grs_all <- 
  alldata %>% 
  filter(Common_name == 'Grey Reef')

```


## Check 
```{r}
glimpse(grs_all)
summary(grs_all$Location)
```
# Filter out by location
```{r}
# Greys tagged at Osprey Reef
os_grs <- alldata %>% 
  filter(Location == 'Osprey') %>% 
  filter(Common_name == 'Grey Reef')

# Greys tagged at Bougainville Reef - 0
br_grs <- alldata %>% 
  filter(installation_name == 'Bougainville') %>% 
  filter(Common_name == 'Grey Reef')

# Greys tagged at Holmes Reef
hr_grs <- alldata %>% 
  filter(installation_name == 'Holmes') %>% 
  filter(Common_name == 'Grey Reef')

# Greys tagged at Flinders Reef
fr_grs <- alldata %>% 
  filter(installation_name == 'Flinders') %>% 
  filter(Common_name == 'Grey Reef')
```


# Large scale movements - do any individuals move between entire reef sites?

##  Will explore using abacus plot, faceted out by installation name (of where receiver was)
```{r fig.height = 10, fig.width = 16}
grs_ab_main <- 
grs_all %>%
  ggplot(mapping = aes(x = detection_timestamp, y = installation_name)) + 
  xlab("Date") + 
  ylab("Tag") +
  geom_point() +
  facet_wrap(~ Serial)
grs_ab_main
```

## Save to get a better look
```{r save-silver-ab}
ggsave(filename = '../output/greys_abacus_overview.png', grs_ab_main , width = 600, height = 200, units = 'mm', dpi = 300)
```

A69-9001-60580 moved from Flinders to Holmes in late November:
```{r}
grs_all %>%
  filter(transmitter_id == "A69-9001-60580") %>% 
  ggplot(mapping = aes(x = detection_timestamp, y = site_code)) + 
  xlab("Date") + 
  ylab("Tag") +
  geom_point()
```

# What about movements a smaller scale? Say between N and S Flinders or E and W Holmes? Or between Osprey wall and lagoon?

## Osprey
```{r fig.height = 10, fig.width = 16}
os_grs %>%
  ggplot(mapping = aes(x = detection_timestamp, y = site_code)) + 
  xlab("Date") + 
  ylab("Tag") +
  geom_point() +
  facet_wrap(~ transmitter_id)
```




# Bougainville cohort
```{r fig.height = 10, fig.width = 16}
br_grs %>%
  ggplot(mapping = aes(x = detection_timestamp, y = installation_name)) + 
  xlab("Date") + 
  ylab("Tag") +
  geom_point() +
  facet_wrap(~ transmitter_id)
```

# Holmes cohort
```{r fig.height = 10, fig.width = 16}
hr_grs %>%
  ggplot(mapping = aes(x = detection_timestamp, y = station_name)) + 
  xlab("Date") + 
  ylab("Tag") +
  geom_point() +
  facet_wrap(~ transmitter_id)
```

 
# Flinders cohort
```{r fig.height = 10, fig.width = 16}
fr_grs %>%
  ggplot(mapping = aes(x = detection_timestamp, y = installation_name)) + 
  xlab("Date") + 
  ylab("Tag") +
  geom_point() +
  facet_wrap(~ transmitter_id)
```

 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 











