---
title: "Data analysis and visualisation - silver tip sharks"
author: "Ben Cresswell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
 html_document:
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 4
    fig_width: 4
    highlight: textmate
    theme: spacelab
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: inline
---


# Set up Rmd
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#rm(list=ls())
```

# Load required packages
```{r packages, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(writexl)
library(readxl)
library(lubridate)
library(tidyverse)
#library(VTrack) # Current R version doesn't like VTrack - may need to install an earlier version..
```

# Load data

```{r}
silvers_all <- alldata %>% 
  filter(Scientific_name == 'Carcharhinus albimarginatus')
```


## Check 
```{r}
glimpse(silvers_all)
summary(silvers_all$Location)
summary(alldata$Location)
```
# Filter out by location
## NOTE: Need to filter by the column "Location" as this is the original tagging location - if you filter by installation_name, you'll only get entries for that
```{r}
# Greys tagged at Osprey Reef
os_silvers <- alldata %>% 
  filter(Location == 'Osprey') %>% 
  filter(Scientific_name == 'Carcharhinus albimarginatus')

# Greys tagged at Bougainville Reef - 0
br_silvers <- alldata %>% 
  filter(str_detect(Location, 'Boug')) %>% 
  filter(Scientific_name == 'Carcharhinus albimarginatus')

# Greys tagged at Holmes Reef
hr_silvers <- alldata %>% 
  filter(str_detect(Location, 'Holm')) %>% 
  filter(Scientific_name == 'Carcharhinus albimarginatus')

# Greys tagged at Flinders Reef
fr_silvers <- alldata %>% 
  filter(str_detect(Location, 'Flin')) %>% 
  filter(Scientific_name == 'Carcharhinus albimarginatus')
```


# Large scale movements - do any individuals move between entire reef sites?

##  Will explore using abacus plot, faceted out by installation name (of where receiver was)
```{r fig.height = 10, fig.width = 16}
silvers_ab_main <- 
silvers_all %>%
  ggplot(mapping = aes(x = detection_timestamp, y = installation_name)) + 
  xlab("Date") + 
  ylab("Tag") +
  geom_point() +
  facet_wrap(~ transmitter_id)
silvers_ab_main
```

## Save to get a better look
```{r save-silver-ab}
ggsave(filename = '../output/silvers_abacus_overview.png', silvers_ab_main , width = 270, height = 100, units = 'mm', dpi = 300)
```

 One individual (A69-9001-64080) moved from Holmes to Flinders to Osprey and then out of array:
```{r}
silvers_all %>%
  filter(transmitter_id == "A69-9001-64080") %>% 
  ggplot(mapping = aes(x = detection_timestamp, y = site_code)) + 
  xlab("Date") + 
  ylab("Tag") +
  geom_point()
```
Should also show up in the Holmes filtered data (assuming tagged there)


# What about movements a smaller scale? Say between N and S Flinders or E and W Holmes? Or between Osprey wall and lagoon?

## Osprey - only 1 individual tagged here
```{r fig.height = 6, fig.width = 10}
#os_silver_ab <- 
  os_silvers %>%
  ggplot(mapping = aes(x = detection_timestamp, y = site_code)) + 
  xlab("Date") + 
  ylab("Tag") +
  geom_point() +
  facet_wrap(~ transmitter_id)
```

## INTERESTING: the one silvertip shark tagged at Osprey appeared to stay in the lagoon for the entire winter period!


```{r}
ggsave(os_silver_ab, filename = "../output/os_silver_abacus.jpg", width = 200, height = 200, units = 'mm', dpi = 400)
```



# Bougainville cohort
```{r fig.height = 10, fig.width = 16}
br_silvers %>%
  ggplot(mapping = aes(x = detection_timestamp, y = installation_name)) + 
  xlab("Date") + 
  ylab("Tag") +
  geom_point() +
  facet_wrap(~ transmitter_id)
```
## 2 individuals - seem very resident



# Holmes cohort - 3 individuals, 2 sticking to their E vs W reefs and one moving around a fair bit
```{r fig.height = 10, fig.width = 16}
hr_silvers %>%
  ggplot(mapping = aes(x = detection_timestamp, y = station_name)) + 
  xlab("Date") + 
  ylab("Tag") +
  geom_point() +
  facet_wrap(~ transmitter_id)
```

 
# Flinders cohort
```{r fig.height = 10, fig.width = 16}
fr_silvers %>%
  ggplot(mapping = aes(x = detection_timestamp, y = station_name)) + 
  xlab("Date") + 
  ylab("Tag") +
  geom_point() +
  facet_wrap(~ transmitter_id)
```

 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 











