---
title: "tidy Mapping"
aauthor: "Ben Cresswell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
 html_document:
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 4
    fig_width: 4
    highlight: textmate
    theme: spacelab
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: inline
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')
#rm(list=ls())
getwd()
```

# Load required packages
```{r packages, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(sp)
library(rgdal)
library(rgeos)
library(adehabitatHR)
library(wesanderson)
library(leaflet)
library(ggmap)    # for fortifying shapefiles
library(readxl)
library(scatterpie)
library(collapse)
library(tidyverse)
```

## Load in shape files for reefs and fortify
```{r shape-files-load, message=FALSE, warning=FALSE, include=FALSE}
# Coral Sea shape files
cs_dryreef_df <- readOGR("../data/3dgbr_geomorph/shape", "coralsea_dryreef") %>% fortify # Don't need dry reef file
cs_reef_df <- readOGR("../data/3dgbr_geomorph/shape", "coralsea_reef") %>% fortify # Can make fillable polygons with this df
#cs_cays_df <- readOGR("../data/3dgbr_geomorph/shape", "coralsea_cay") %>% fortify # Don't need the cays for this scale of mapping

# GBR
#gbr_dryreef_df <- readOGR("../data/3dgbr_geomorph/shape", "gbr_dryreef") %>% fortify # gbr_dryreef is too big and just duplicates the feats file
gbr_feats_df <- readOGR("../data/3dgbr_geomorph/shape", "gbr_features") %>% fortify # Outlines of main reefs
gbr_shelf_df <- readOGR("../data/3dgbr_geomorph/shape", "gbr_shelf") %>% fortify # Includes inshore detail (so can use to map coastline better than straya object)

# Park boundaries - don't need for this as we are so zoomed in they aren't captured
#csmp_df <- readOGR("../data/3dgbr_geomorph/shape", "qld_gbrwha_cscz") %>% fortify
#gbr_df <- readOGR("../data/3dgbr_geomorph/shape", "gbrwha_outer") %>% fortify
```


# Other wrangling
Tagging information:
Can use the project_tags_all df but just need to make summary of how many were tagged in each location
```{r}
source("../code/project_tag_list.R")
#glimpse(project_tags_all)
```


# First need to summarise by reef and figure out numbers per reef 
project_tags_all has a column called 'Location' but this has sites at a smaller scale than we want here (e.g. 'Flinders - South' instead of just 'Flinders') so we'll make a column that just has the overall installation  recorded
```{r}
installation_sum <- 
project_tags_all %>% 
  #group_by(Location) %>%
  mutate(installation_name = factor(case_when(grepl("Osprey", Location) ~ 'Osprey',
                                              grepl("Bougain", Location) ~ 'Bougainville',
                                              grepl("Holmes", Location) ~ 'Holmes',
                                              grepl("Flind", Location) ~ 'Flinders'))) %>% 
  filter(Type != "press") %>%                                                               # Don't want duplicate temp and press
  count(installation_name, Org_type) 
installation_sum
```

# Relevel installation name by North to South if required
```{r}
installation_sum <- installation_sum %>% 
  mutate(installation_name = fct_relevel(installation_name, c('Osprey', 'Bougainville', 'Holmes', 'Flinders')))
```



# Fill in 0s and calculate totals 
```{r}
installation_sum <- installation_sum %>% 
  tidyr::complete(installation_name, Org_type) %>% 
  replace(is.na(.), 0) %>% 
  pivot_wider(names_from = Org_type, values_from = c(n)) %>% 
  mutate_if(is.integer, as.numeric) %>% 
  mutate(Total = Teleost+Elasmobranch)
installation_sum
```

# Need to add in some other variables for plotting
```{r}
installation_sum <- installation_sum %>% 
  mutate(reef_lat = case_when(grepl("Osprey", installation_name) ~ -13.88,             # Lat/long: For actual reefs (not split out by N vs S)
                       grepl("Bougain", installation_name) ~ -15.5,
                       grepl("Holmes", installation_name) ~ -16.48,
                       grepl("Flind", installation_name) ~ -17.58),
         reef_long = case_when(grepl("Osprey", installation_name) ~ 146.60,
                        grepl("Bougain", installation_name) ~ 147.1,
                        grepl("Holmes", installation_name) ~ 147.98,
                        grepl("Flind", installation_name) ~ 148.45)) %>% 
  mutate(point_lat = case_when(grepl("Osprey", installation_name) ~ -14.2,              # Lat/long: For point locations
                        grepl("Bougain", installation_name) ~ -15.5,
                        grepl("Holmes", installation_name) ~ -15.9,
                        grepl("Flind", installation_name) ~ -17.2),
         point_long = case_when(grepl("Osprey", installation_name) ~ 148,
                         grepl("Bougain", installation_name) ~ 146.6,
                         grepl("Holmes", installation_name) ~ 148.5,
                         grepl("Flind", installation_name) ~ 147)) %>%
  mutate(label = c("b", "d", "c", "a")) %>%          # Labels (reef names won't fit on plot) - don't actually need this as we'll colour code
  mutate(label_lat = point_lat + 0.23,                                                  # Lat/long: For reef labels
         label_long = point_long)

installation_sum
```



# Plots

# Basemap
```{r}
tag_effort_basemap <- 
  ggplot() +
  geom_path(data = gbr_shelf_df, aes(x = long, y = lat, group = group), color = 'grey20', size = .2) +
  geom_polygon(data = gbr_feats_df, aes(x = long, y = lat, group = group), fill = 'grey50', size = .1) +                # Reefs grey75 but this layer masked by the alpha from the shelf layer
  geom_polygon(data = gbr_shelf_df, aes(x = long, y = lat, group = group), fill = 'grey90', size = .1,  alpha = .4) +   # .. and makes the land be grey50
  geom_path(data = gbr_feats_df, aes(x = long, y = lat, group = group), color = 'grey20', size = .1) +
  geom_polygon(data = cs_reef_df, aes(x = long, y = lat, group = group), color = 'black', fill = 'gray75', size = .2) + # Reefs  grey75 
  theme(axis.title = element_blank(), 
        axis.text.x.top = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        #axis.ticks.x.top = element_line(), 
        #panel.grid = element_line(colour = "#ECEFF1"),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent", colour = "transparent")) +
  scale_x_continuous(position = "top") +
  coord_quickmap(ylim = c(-18, -13.5), xlim = c(143, 149))
tag_effort_basemap
ggsave('../output/tag-effort-map-draft.png', tag_effort_basemap, width = 220, height = 180, units = "mm")
```

# Bubble map
```{r bubble-fig, fig.height=6, fig.width=6, message=FALSE, warning=FALSE}
bubble_fig <- 
  tag_effort_basemap +
  geom_segment(data = installation_sum, aes(x = reef_long, y = reef_lat, xend = point_long, yend = point_lat), size = .3,  col = "black") +
  geom_polygon(data = cs_reef_df, aes(x = long, y = lat, group = group), color = 'black', fill = 'gray75', size = .2) +
  geom_point(data = installation_sum, aes(x = point_long, y = point_lat, size = Total, fill = installation_name), stroke = 0.5, pch = 21) +
  scale_size(range = c(12, 65)) +  # Set the same as the range in the data
  #scale_fill_brewer(palette = "Dark2") +
  #scale_fill_viridis_d(direction = -1) +
  #scale_fill_manual(values=wes_palette(name="Moonrise3", n = 4, type = "discrete")) +
  scale_shape_manual(name = 'Reef') +
  scale_fill_manual(values =  installation_palette) +
  #geom_text(data = installation_sum, aes(x = label_long , y = label_lat, label = label), size = 6, fontface = "plain" ) +
  geom_text(data = installation_sum, aes(x = point_long, y = point_lat, label = Total), size = 6, fontface = "bold") +
  #geom_text(data = installation_sum, aes(x = long1, y = lat1 + 0.23, label = label), size = 4) +
  #theme(legend.position = 'none') +
  theme(legend.key = element_blank(),
        legend.background = element_rect(fill = "transparent"),
        legend.title = element_blank(),
        legend.text = element_text(size = 12),
        #legend.key.size = unit(10, 'cm'), #change legend key size
        #legend.key.height = unit(10, 'cm'), #change legend key height
        #legend.key.width = unit(10, 'cm'), #change legend key width
        legend.position = c(0.16, 0.55)) +
  guides(size = "none") +
  guides(fill = guide_legend(override.aes = list(size=15))) +
  coord_quickmap(ylim = c(-18, -13.5), xlim = c(143.5, 149)) 


bubble_fig
#ggsave('../output/tag-bubble-draft.png', bubble_fig, width = 220, height = 180, units = "mm")

```


# Need Australia inset map
```{r}
straya <- 
  map_data("world") %>% 
  filter(region == 'Australia') %>% 
  ggplot() +
  geom_polygon(aes(x = long, y = lat, group = group), colour = 'black', fill = 'grey10', lwd = 0.3) +
  theme(axis.title = element_blank(), 
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_line(colour = "transparent"),
        panel.border = element_rect(colour = "transparent", fill = "transparent"),
        panel.background = element_rect(fill = "transparent", colour = "transparent"),
        plot.background = element_rect(fill = "transparent", colour = "transparent")) +
  geom_rect(aes(xmin = 143, xmax = 149, ymin = -18, ymax = -13.5), color = "white", fill = 'transparent', lwd = 0.25) +
  coord_quickmap(ylim = c(-44, -9), xlim = c(114, 152)) 
straya
```



# Combine
```{r final-tag-plot, fig.width = 10, fig.height = 6, out.height =}
tagging_effort_map <- 
bubble_fig +
  annotation_custom(ggplotGrob(straya), xmin = 143, xmax = 146, ymin = -18.2, ymax = -16.5) +
  scalebar(cs_dryreef_df, dist = 100, dist_unit = "km", transform = TRUE, model = "WGS84",            # Geo properties
           location = 'bottomright', anchor = c(x = 149, y = -18.1),                                # Position of bar
           family = "Arial", st.size = 4, st.dist = 0.006,                                            # Text properties
           height = 0.005, border.size = 0.5, st.bottom = FALSE) +                                     # Bar properties
  draw_image('../data/North_Pointer.jpg', x = 148.5, y = -14.2, scale = 0.35)
tagging_effort_map
```

# Save
```{r}
ggsave("../output/tagging_effort_map.png", plot = tagging_effort_map, width = 220, height = 180, units = "mm")
```











