---
title: "tidy Mapping"
aauthor: "Ben Cresswell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
 html_document:
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 4
    fig_width: 4
    highlight: textmate
    theme: spacelab
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: inline
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#rm(list=ls())
getwd()
```


Note: Need to run the tidyeda.Rmd first to subset the required objects

# Load required packages
```{r packages, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(sp)
library(rgdal)
library(rgeos)
library(adehabitatHR)
library(leaflet)
library(ggmap)    # for fortifying shapefiles
library(readxl)
library(scatterpie)
library(collapse)
library(tidyverse)
```

# First need a base map

## Load world map object from ggplot
```{r world-map-load}
world <- map_data("world")
```

## Plot the map trimmed down to just GBR and Coral Sea area
```{r}
base_map <- 
  world %>% 
  ggplot() +
  geom_polygon(aes(x = long, y = lat, group = group), fill = "#78909C") +
  coord_map(orientation = c(90,0, 150), ylim = c(-25, -13), xlim = c(145, 155)) 
print(base_map)
```


Looking about right. Now need to get Coral Sea reefs on this map.

## Load in shape files from 3dgbr using ggmap
```{r shape-files-load, message=FALSE, warning=FALSE}
cs_dryreef <- readOGR("../data/3dgbr_geomorph/shape", "coralsea_dryreef")
cs_reef <- readOGR("../data/3dgbr_geomorph/shape", "coralsea_reef")
#cs_cays <- readOGR("../data/3dgbr_geomorph/shape", "coralsea_cay")
#gbr_dryreef <- readOGR("../data/3dgbr_geomorph/shape", "gbr_dryreef")
#gbr_feats <- readOGR("../data/3dgbr_geomorph/shape", "gbr_features")
#gbr_shelf <- readOGR("../data/3dgbr_geomorph/shape", "gbr_shelf")
```

## These can't be plotted directly in ggplot so need to be converted to dataframes:
```{r message=FALSE}
cs_dryreef_df <- fortify(cs_dryreef)
cs_reef_df <- fortify(cs_reef)
#cs_cays_df <- fortify(cs_cays)
#gbr_dryreef_df <- fortify(gbr_dryreef)
#gbr_feats_df <- fortify(gbr_feats)
#gbr_shelf_df <- fortify(gbr_shelf)
```


# Now the shapefile can be plotted as either a geom_path or a geom_polygon.
# Paths handle clipping better. Polygons can be filled.
# You need the aesthetics long, lat, and group.

# Could plot all the shapefiles...
```{r}
base_map +
    #geom_path(data = gbr_dryreef_df, aes(x = long, y = lat, group = group), color = 'gray', fill = 'white', size = .2) +
    #geom_path(data = gbr_feats_df, aes(x = long, y = lat, group = group), color = 'gray', fill = 'white', size = .2) +
    #geom_path(data = gbr_shelf_df, aes(x = long, y = lat, group = group), color = 'gray', fill = 'white', size = .2) +
    geom_polygon(data = cs_reef_df, aes(x = long, y = lat, group = group), color = 'gray', fill = 'white', size = .2) + # Can use fill = on polygon but not path
    #geom_path(data = cs_cays_df, aes(x = long, y = lat, group = group), color = 'gray', fill = 'white', size = .2) +
    geom_path(data = cs_dryreef_df, aes(x = long, y = lat, group = group), color = 'gray', size = .2)

```

Too much going on with this. For our purposes we'll wrangle out just the northern reefs components of the cs_reef and cs_dryreef dfs. This will allow us to both zoom in to the these reefs and also expand the map without including the other reefs.


```{r}
reefs_north <- cs_reef_df %>% 
  filter(long < 149) %>% 
  filter(lat > -18)

dryreefs_north <- cs_dryreef_df %>% 
  filter(long < 149) %>% 
  filter(lat > -18)
```

# Let's redefine a basemap for just the northern reefs:
```{r}
northern_map <- 
ggplot() +
  geom_polygon(data = world, aes(x = long, y = lat, group = group), color = "black", fill = 'grey', lwd = 0.3)+
  coord_map(orientation = c(90,0, 150), ylim = c(-17.8, -13.2), xlim = c(145, 150)) 
northern_map
```

# And add in the reefs
```{r}
nreefsmap <- 
northern_map +
    geom_polygon(data = reefs_north, aes(x = long, y = lat, group = group), color = 'grey30', fill = 'grey', lwd = 0.3) +
    #geom_polygon(data = dryreefs_north, aes(x = long, y = lat, group = group), color = 'black', fill = 'grey') +
    theme(#axis.title = element_blank(), 
        #axis.text = element_blank(),
        #axis.ticks = element_blank(),
        #panel.grid = element_line(colour = "#ECEFF1"),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent", colour = "transparent"))
nreefsmap
```



# Add in bubble plot for # individuals tagged per location

Can use the project_tag_list df but just need to make summary of how many were tagged in each location


```{r}
source("../code/project_tag_list.R")
glimpse(project_tag_list)
```






# First need to summarise by reef and figure out numbers per reef 
project_tag_list has a column called 'Location' but this has sites at a smaller scale than we want here (e.g. 'Flinders - South' instead of just 'Flinders') so we'll make a column that just has the overall reef site recorded
```{r}
locsum <- 
project_tag_list %>% 
  #group_by(Location) %>%
  mutate(Reef = factor(case_when(grepl("Osprey", Location) ~ 'Osprey',
                         grepl("Bougain", Location) ~ 'Bougainville',
                         grepl("Holmes", Location) ~ 'Holmes',
                         grepl("Flind", Location) ~ 'Flinders'))) %>% 
  count(Reef, Org_type) 
locsum
```
# Another df with values assigned to each organism type, teleost vs elasmo (inc 0)
```{r}
locsum <- locsum %>% 
  tidyr::complete(Reef, Org_type) %>% 
  #group_by(Reef, lat, long) %>% 
  replace(is.na(.), 0) %>% 
  pivot_wider(names_from = Org_type, values_from = c(n)) %>% 
  mutate_if(is.integer, as.numeric)
locsum
```


# And add back in the totals 
```{r}
locsum<- locsum %>% 
 mutate(Total = Teleost+Elasmobranch)
locsum

```



# Need to specify lats and longs for overall reefs (not split out by North or South etc)
```{r}
locsum <- 
locsum %>% 
mutate(lat = case_when(grepl("Osprey", Reef) ~ -13.88,
                       grepl("Bougain", Reef) ~ -15.5,
                       grepl("Holmes", Reef) ~ -16.48,
                       grepl("Flind", Reef) ~ -17.58),
       long = case_when(grepl("Osprey", Reef) ~ 146.60,
                        grepl("Bougain", Reef) ~ 147.1,
                        grepl("Holmes", Reef) ~ 147.98,
                        grepl("Flind", Reef) ~ 148.45
                          ))
```


# And need to specify separate positions for the points to be located 
```{r}
locsum <- 
locsum %>% 
mutate(lat1 = case_when(grepl("Osprey", Reef) ~ -14,
                        grepl("Bougain", Reef) ~ -15.25,
                        grepl("Holmes", Reef) ~ -16,
                        grepl("Flind", Reef) ~ -17),
       long1 = case_when(grepl("Osprey", Reef) ~ 149.5,
                         grepl("Bougain", Reef) ~ 149.5,
                         grepl("Holmes", Reef) ~ 149.5,
                         grepl("Flind", Reef) ~ 149.5))
```


```{r}
fish_cols = c("#5dfdcb", "#7cc6fe")
```

```{r}
locsum
```


```{r bubble-fig, fig.height=6, fig.width=10}
bubble_fig <- 
nreefsmap +
  geom_segment(data = locsum, aes(x = long, y = lat, xend = long1, yend = lat1), size = .3,  col = "black") +
  geom_polygon(data = reefs_north, aes(x = long, y = lat, group = group), color = 'grey30', fill = 'grey', lwd = 0.3) + # reefs over top of lines
  geom_point(data = locsum, aes(x = long1, y = lat1, size = Total), fill = "white", col = "black", stroke = 0.5, pch = 21) +
  scale_size(range = c(4, 35)) +
  geom_text(data = locsum, aes(x = long1+1 , y = lat1+0.2, label = Reef)) +
  geom_text(data = locsum, aes(x = long1+1, y = lat1-0.1, label = Total)) +
  theme(legend.position = 'none') +
  coord_map(ylim = c(-17.8, -13.2), xlim = c(145, 151)) 
```

# Save
```{r}
ggsave("../output/tagging_effort.png", plot = bubble_fig, width = 174, height = 120, units = "mm")
```



# Bubble scatter pie plot
```{r pie-fig, fig.height=8, fig.width=8}
#pie_fig <- 
nreefsmap +
  geom_segment(data = locsum, aes(x = long, y = lat, xend = long1, yend = lat1), size = .3,  col = "black") +
  geom_scatterpie(data = locsum, aes(x=long1, y=lat1, group = Reef, r = Total/100), cols = c('Teleost', 'Elasmobranch'), lwd = 0.3) +
  scale_fill_manual(values = fish_cols) +
  theme(legend.position = 'none')
```

