---
title: "Mapping the big movers"
aauthor: "Ben Cresswell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
 html_document:
    code_folding: show
    collapse: no
    fig_height: 4
    df_print: paged
    fig_caption: yes
    highlight: textmate
    theme: spacelab
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: inline
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = '')
                      #fig.width = 7, fig.height = 7
                      
options(knitr.duplicate.label = 'allow')
#rm(list=ls())
#getwd()
```


# Load required packages
```{r packages, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(sp)
library(rgdal)
library(rgeos)
library(adehabitatHR)
library(leaflet)
library(cowplot)
library(ggpubr)   # Figure creation including separate legends
library(ggmap)    # for fortifying shapefiles
library(ggsn)     # Package with built in scale bar and north point
library(readxl)
library(scatterpie)
library(collapse)
library(tidyverse)
library(rayshader)
```


# Load data

## Shape files for reefs and fortify
```{r shape-files-load, message=FALSE, warning=FALSE, include=FALSE}
# Coral Sea shape files
cs_dryreef_df <- readOGR("../data/3dgbr_geomorph/shape", "coralsea_dryreef") %>% fortify
cs_reef_df <- readOGR("../data/3dgbr_geomorph/shape", "coralsea_reef") %>% fortify 

# GBR
#gbr_feats_df <- readOGR("../data/3dgbr_geomorph/shape", "gbr_features") %>% fortify # Outlines of main reefs
gbr_shelf_df <- readOGR("../data/3dgbr_geomorph/shape", "gbr_shelf") %>% fortify # Includes inshore detail (so can use to map coastline better than straya object)
#gbr_dry <- readOGR("../data/3dgbr_geomorph/shape", "gbr_dryreef") %>% fortify # Waaaay to big to plot

# Park boundaries - don't need for this as we are so zoomed in they aren't captured
csmp_df <- readOGR("../data/3dgbr_geomorph/shape", "qld_gbrwha_cscz") %>% fortify
gbr_df <- readOGR("../data/3dgbr_geomorph/shape", "gbrwha_outer") %>% fortify
```


## Tagging locations and movements
Need to run the wrangling script:
```{r run-wrangle, message=FALSE, warning=FALSE, include=FALSE}
source(knitr::purl("wrangling_bigmovers.Rmd", quiet=TRUE))
```



# Plotting


### Inset maps

#### Inset  1: Australia overview 
```{r straya-map}
straya <- 
  map_data("world") %>% 
  filter(region == 'Australia') %>% 
  ggplot() +
  geom_polygon(aes(x = long, y = lat, group = group), colour = 'black', fill = 'grey10', lwd = 0.3) +
  theme(axis.title = element_blank(), 
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_line(colour = "transparent"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent", colour = "transparent")) +
  geom_rect(aes(xmin = 143, xmax = 153, ymin = -24, ymax = -10), color = "white", fill = 'transparent', lwd = 0.25) +
  coord_quickmap(ylim = c(-45, -8), xlim = c(112, 154)) 
#straya
```


#### Inset 2: Tagging locations
Need to carve up the cs_reef and dry_reef objects first:
```{r}
cs_dryreef_E <- cs_dryreef_df %>% filter(long >149)
cs_reef_W <- cs_reef_df %>% filter(long <149)
```

Then plot
```{r tagging-map}
taggingmap <- 
map_data("world") %>% filter(region == 'Australia') %>% filter(lat > -25) %>% # E Coast
 ggplot() +
  geom_polygon(data = csmp_df, aes(x = long, y = lat, group = group), fill = "white", color = 'grey20', size = 0.5, linetype = "dotdash") + 
  geom_path(data = gbr_df, aes(x = long, y = lat, group = group), color = 'grey20', size = 0.5, linetype = "dotdash") +
  geom_polygon(aes(x = long, y = lat, group = group), colour = 'grey20', fill = 'grey50', lwd = 0.5) +
  geom_polygon(data = cs_dryreef_E, aes(x = long, y = lat, group = group), fill = 'grey75', colour ='grey45', size = .2) +
  geom_polygon(data = cs_reef_W, aes(x = long, y = lat, group = group), fill = 'grey75', colour ='grey45', size = .2) +
  geom_point(data = tag_locs_tigers, aes(x = Long, y = Lat, shape = Scientific_name, fill = sharkloc), size = 4) +
  geom_point(data = tag_locs_others, aes(x = Long, y = Lat, shape = Scientific_name, fill = sharkloc), size = 4) +
  scale_shape_manual(name = 'Shark ID', values = c(22, 24, 21)) +
  scale_fill_brewer(name = 'Shark ID', palette = "Dark2", direction = -1) +
  theme(legend.position = 'none') +
  #guides(fill = guide_legend(override.aes = list(pch = c(24,24,22,21,21,21)))) +
  #guides(shape = "none") +
  theme(axis.title = element_blank(), 
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        panel.background = element_rect(fill = "transparent"),
        #legend.key = element_blank(),
        #legend.background = element_rect(fill = "transparent"),
        #legend.title = element_blank(),
        #legend.position = "left"),
        plot.background = element_rect(fill = "transparent", colour = "transparent"))+
  coord_quickmap(ylim = c(-23.8, -10), xlim = c(143, 153)) 
taggingmap

ggsave(taggingmap, filename = '../output/bigmovers-tagmap.png', width = 62, height = 100, units = 'mm', dpi = 400)
```

Squares are silvertips
Triangles are greys
Circles are tigers


### Inset 3: Legend
```{r make-legend}
source("legend_bigmovers.R")
legend_bigmov
```




### Inset 4: Zoom on Flinders and Holmes
```{r bigmov-zoom-map, message=FALSE, warning=FALSE}
zoom_map <- 
 ggplot() +
  geom_polygon(data = cs_reef_df, aes(x = long, y = lat, group = group), fill = "grey", color = 'black', size = .2) + 
  geom_curve(data = tiger_sublocmovs, aes(x = From_Long, y = From_Lat, xend = To_Long, yend = To_Lat, colour = sharkloc), lty = "11", size = 1, size = 1, angle = 90, curvature = 0.45, arrow = arrow(length = unit(0.3, "cm"), type="closed")) +
  geom_curve(data = other_sublocmovs, aes(x = From_Long, y = From_Lat, xend = To_Long, yend = To_Lat, colour = sharkloc), lty = "solid",  size = 1, size = 1, angle = 90, curvature = 0.45, arrow = arrow(length = unit(0.3, "cm"), type="closed")) +
  scale_colour_brewer(palette = "Dark2", direction = -1) +
  #scale_colour_viridis_d() +                                                        # viridis colour option
  guides(colour = 'none', fill = 'none', shape = 'none') +                           # Don't want any legend
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank(),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        panel.background = element_rect(fill = "white"),
        plot.background = element_rect(fill = "transparent", colour = "transparent")) +
  coord_quickmap(ylim = c(-18.2, -16.1), xlim = c(147.5, 149)) 
  
#zoom_map
```
## Zoom inset explanation:
A69-9001-63847	Galeocerdo cuvier	            2021-03-16	Capricorn Bunkers	->  Holmes - West     |	2021-07-13	Holmes - West	   -> Flinders - North
A69-9001-64080	Carcharhinus albimarginatus	  2021-02-22  Holmes - West	    ->  Flinders - North  | 2021-03-25	Flinders - North ->	Osprey	
A69-9001-60580	Carcharhinus amblyrhynchos	  2021-10-24  Flinders - South  ->	Holmes - East	
A69-9001-63947	Galeocerdo cuvier           	2021-08-10	Palm Islands      ->	Flinders - North

# Save if required
```{r}
#ggsave(zoom_map, filename = "../output/bigmove-zoomed.jpg", width = 62, height = 100, units = 'mm')
```


### Plot
```{r}
mov_base_map <- 
 map_data("world") %>% 
  filter(region == 'Australia') %>% 
  filter(lat > -25) %>% 
 ggplot() +
  geom_polygon(aes(x = long, y = lat, group = group), fill = "grey50", colour = "grey20", size = 0.3) +
  #geom_path(data = gbr_shelf_df, aes(x = long, y = lat, group = group), color = 'grey20', size = 0.5) +
  geom_polygon(data = cs_dryreef_E, aes(x = long, y = lat, group = group), fill = 'grey75', colour ='grey45', size = 0.5) +
  geom_polygon(data = cs_reef_W, aes(x = long, y = lat, group = group), fill = 'grey80', colour ='grey45', size = 0.5) +
  theme(axis.title = element_blank(), 
        #axis.text = element_blank(),
        #axis.ticks = element_blank(),
        #panel.grid = element_line(colour = "#ECEFF1"),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent", colour = "transparent")) +
  coord_quickmap(ylim = c(-23.8, -10), xlim = c(143.5, 158.2))  # geom_curve doesn't play nicely with coord_map 
mov_base_map
```






# Now make movement map using the two separate dfs for shark movement
```{r message=FALSE, warning=FALSE}
bigmov_map <- 
  mov_base_map +
  geom_curve(data = other_locmovs, aes(x = From_Long, y = From_Lat, xend = To_Long, yend = To_Lat, colour = sharkloc),
          lty = "solid", size = 1, angle = 100, curvature = 0.5 , arrow = arrow(length = unit(0.3, "cm"), type="closed")) +
  geom_curve(data = tiger_locmovs, aes(x = From_Long, y = From_Lat, xend = To_Long, yend = To_Lat, colour = sharkloc),
          lty = "11",  size = 1, angle = 50, curvature = 0.25, arrow = arrow(length = unit(0.3, "cm"), type="closed")) +
  scale_colour_brewer(palette = "Dark2", direction = -1) +
  #scale_colour_viridis_d() +                                                                                                              # viridis colour option
  guides(fill = 'none', colour = 'none') +
  labs(colour = "Individual ID") +
  theme(legend.text = element_text(face = "italic"),
        legend.position = c(.8,.8)) +
  geom_rect(aes(xmin = 147.5, xmax = 149, ymin = -18.2, ymax = -16.1), color="grey50", fill = 'transparent')+
  coord_quickmap(ylim = c(-24, -10), xlim = c(143, 158))  # geom_curve doesn't play nicely with coord_map 
bigmov_map
#ggsave(bigmov_map, filename = '../output/bigmovers_mainmap.png', width = 200, height = 200, units = 'mm', dpi = 400)
```



```{r}
#ggsave(bigmov_map, filename = '../output/movement_mapV2.png', width = 200, height = 200, units = 'mm', dpi = 400)
```










```{r}
bigmov_zoom <- 
  bigmov_map + annotation_custom(ggplotGrob(zoom_map), 
    xmin = 151, xmax = 159.5, ymin = -24, ymax = -15)
bigmov_zoom
ggsave(bigmov_zoom, filename = "../output/bigmove-zoom.jpg", width = 200, height = 200, units = 'mm')
```








# Add overview map, scale bar and N pointer
```{r final-fig}
bigmov_final <- 
  bigmov_map +
  annotation_custom(ggplotGrob(zoom_map),  xmin = 151, xmax = 159.5, ymin = -24, ymax = -16 ) +
  annotation_custom(ggplotGrob(taggingmap),  xmin = 150, xmax = 162 , ymin = -15.5, ymax = -9.8) +
  annotation_custom(ggplotGrob(straya), xmin = 141, xmax = 148, ymin = -24.5, ymax = -21) +
  scalebar(cs_dryreef_df, dist = 200, dist_unit = "km", transform = TRUE, model = "WGS84", height = 0.008, 
           location = 'bottomright', anchor = c(x = 157, y = -24.4), family = "Arial", st.size = 3.2, border.size = 0.4, st.bottom = FALSE) +
  draw_image('../data/North_Pointer.jpg', x = 144.2, y = -21, scale = 1.5)
#bigmov_final
ggsave(bigmov_final, filename = "../output/bigmover_fig_final.jpg", width = 200, height = 200, units = 'mm')

```











## PLOTTING WITH ALL ELEMENTS SEPARATELY ##

```{r message=FALSE, warning=FALSE}
bigmov_map2 <- 
  reefsmap +
  geom_curve(data = other_locmovs, aes(x = From_Long, y = From_Lat, xend = To_Long, yend = To_Lat, colour = shark_id),
          lty = "solid", size = 1, angle = 100, curvature = 0.5 , arrow = arrow(length = unit(0.3, "cm"), type="closed")) +
  geom_curve(data = tiger_locmovs, aes(x = From_Long, y = From_Lat, xend = To_Long, yend = To_Lat, colour = shark_id),
          lty = "11",  size = 1, angle = 50, curvature = 0.25, arrow = arrow(length = unit(0.3, "cm"), type="closed")) +
  scale_colour_brewer(palette = "Dark2", direction = -1) +
  #scale_colour_viridis_d() +                                                                                                              # viridis colour option
  guides(fill = 'none', colour = 'none') +
  labs(colour = "Individual ID") +
  theme(legend.text = element_text(face = "italic"),
        legend.position = c(.8,.8)) +
  geom_rect(aes(xmin = 147.5, xmax = 149, ymin = -18.2, ymax = -16.1), color="grey50", fill = 'transparent')+
  coord_quickmap(ylim = c(-24, -10), xlim = c(143, 154)) +  # geom_curve doesn't play nicely with coord_map 
  annotation_custom(ggplotGrob(straya), xmin = 141, xmax = 148, ymin = -24.5, ymax = -21) +
  scalebar(cs_dryreef_df, dist = 200, dist_unit = "km", transform = TRUE, model = "WGS84", height = 0.008, 
           location = 'bottomright', anchor = c(x = 150.2, y = -24.2), family = "Arial", st.size = 3.2, border.size = 0.4, st.bottom = FALSE) +
  draw_image('../data/North_Pointer.jpg', x = 144.2, y = -21, scale = 1.5)
bigmov_map2
ggsave(bigmov_map2, filename = '../output/bigmove_map2.png', width = 125, height = 200, units = 'mm', dpi = 400)

```








### MAPPING ARCHIVE CODE ###

```{r}





reefsmap +
  geom_curve(data = mover_sum_sublocation, aes(x = From_Long, y = From_Lat, xend = To_Long, yend = To_Lat, colour = transmitter_id),
             size = 1, angle = 100, curvature = 0.3, arrow = arrow(length = unit(0.3, "cm"), type="closed")) +
  geom_point(data = tag_locs, aes(x = Long, y = Lat, shape = Scientific_name, fill = transmitter_id), size = 4) +
  scale_shape_manual(values = c(21, 22, 24)) +
  guides(colour = 'none', fill = 'none', shape = 'none') +                           # Don't want any legend
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        panel.background = element_rect(fill = "white"),
        plot.background = element_rect(fill = "transparent", colour = "transparent")) +
  coord_quickmap(ylim = c(-18.2, -16.1), xlim = c(147.5, 149)) # geom_curve doesn't play nicely with coord_map 

```



