---
title: "Map  for Flinders and Holmes Reefs intra-movements"
aauthor: "Ben Cresswell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
 html_document:
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 4
    fig_width: 4
    highlight: textmate
    theme: spacelab
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: inline
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#rm(list=ls())
getwd()
```


# Load required packages
```{r packages, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(sp)
library(rgdal)
library(rgeos)
library(adehabitatHR)
library(leaflet)
library(ggmap)    # for fortifying shapefiles
library(readxl)
library(scatterpie)
library(collapse)
library(tidyverse)
```

# First need to specify data from which to draw Flinders and Holmes reef area data
Only really need to do this to exclude reefs to the east from the map so you can open the figure up to the RHS and put embedded figures in
```{r read-flinholm-data, message=FALSE, warning=FALSE}
flinholm_reef <- 
  readOGR("../data/3dgbr_geomorph/shape", "coralsea_dryreef") %>% 
  fortify() %>% 
  filter(long < 150) %>% 
  filter(lat > -18)
```

# And now can plot base map
```{r}
flinholm_base <- 
  flinholm_reef %>%   
  ggplot() +
  geom_polygon(aes(x = long, y = lat, group = group), color = 'grey30', fill = 'grey', lwd = 0.3) +
  coord_quickmap(ylim = c(-18, -16.35), xlim = c(147.6, 148.7)) +
  theme(axis.title = element_blank(), 
        #axis.text = element_blank(),
        #axis.ticks = element_blank(),
        #panel.grid = element_line(colour = "#ECEFF1"),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent", colour = "transparent")) 

flinholm_base
```




## Load receiver locations

```{r}
site_list <- read_excel("../data/receiver_list_dep1.xlsx") %>% 
  mutate_if(is.character, as.factor) %>% 
  dplyr::select(station_name, station_name_long, station_latitude, station_longitude)
```



## Can plot labels directly on map within circles (points)
First need to shorten labels
```{r}
site_list <-
  site_list %>% 
  mutate(station_name = str_sub(station_name, 4, -1))
site_list
```



## Plot - points directly on receiver locations:
```{r flinholm-sites, fig.width = 6, fig.height = 6}
flinholm_vr2s <- 
  flinholm_base +
  geom_point(data = site_list, aes(x = station_longitude, y =station_latitude), colour = 'grey10', fill = 'lightskyblue', size = 8,  stroke = 0.3, shape = 21 )+
  geom_text(data = site_list, aes(x = station_longitude, y =station_latitude, label = station_name), size = 3)
flinholm_vr2s
```

# Or.. we can plot labels offset from actual locations. We'll need to specify these first
```{r}
site_list <-
  site_list %>% 
  mutate(label_long = case_when(
    grepl("H1", station_name) ~ 148.5,
    grepl("H2", station_name) ~ 148.5,
    grepl("H3", station_name) ~ 148.5,
    grepl("H4", station_name) ~ 148.5,
    grepl("F1", station_name) ~ 147.8,
    grepl("F2", station_name) ~ 147.8,
    grepl("F3", station_name) ~ 147.8,
    grepl("F4", station_name) ~ 147.8,
    grepl("F5", station_name) ~ 147.8,
    grepl("F6", station_name) ~ 147.8,
    ),
         label_lat = case_when(
    grepl("H1", station_name) ~ -16.7,
    grepl("H2", station_name) ~ -16.6,
    grepl("H3", station_name) ~ -16.5,
    grepl("H4", station_name) ~ -16.4,
    grepl("F1", station_name) ~ -18.0,
    grepl("F2", station_name) ~ -17.9,
    grepl("F3", station_name) ~ -17.8,
    grepl("F4", station_name) ~ -17.6,
    grepl("F5", station_name) ~ -17.5,
    grepl("F6", station_name) ~ -17.4))

site_list
```





## Plot - points offset
```{r flinholm-sites, fig.width = 7, fig.height = 7}
flinholm_vr2s <- 
  flinholm_base +
  geom_segment(data = site_list, aes(x = station_longitude, y =station_latitude, xend = label_long, yend = label_lat), colour = 'grey') +
  geom_point(data = site_list, aes(x = label_long, y = label_lat), colour = 'grey10', fill = 'lightskyblue', size = 8,  stroke = 0.3, shape = 21 )+
  geom_text(data = site_list, aes(x = label_long, y = label_lat, label = station_name), size = 3) +
  geom_polygon(data = flinholm_reef, aes(x = long, y = lat, group = group), color = 'grey30', fill = 'grey', lwd = 0.3) 

flinholm_vr2s
```



## NOTES FOR MOVING THIS FORWARD (breadcrumbs!)

Maybe don't need the VR2W labels at all....?
Given that we are now focusing in on these 2 reef complexes, maybe we need to go back to alldata and extract all individuals that were tagged on these reefs and plot their tracks...  Arrows/curves aren't going to work that well though so need to think about how to visualise this nicely... Hmmmmm....





## Add movement curves for the big movers
```{r flin-holm, fig.width = 6, fig.height = 6}
flinholm_movers <- 
  flinholm_base + 
   geom_curve(data = mover_sum_reef2, aes(x = From_Long, y = From_Lat, xend = To_Long, yend = To_Lat, colour = transmitter_id),
             size = 1, angle = 90, curvature = 0.4, arrow = arrow(length = unit(0.2, "cm"), type="closed")) +
  scale_color_viridis_d()
flinholm_movers
```


## More detail
```{r flin-holm, fig.width = 6, fig.height = 6}
flinholm_vr2s +
   geom_curve(data = holmes_movers, aes(x = From_Long, y = From_Lat, xend = To_Long, yend = To_Lat, colour = transmitter_id),
             size = 1, angle = 90, curvature = 0.4, arrow = arrow(length = unit(0.3, "cm"), type="closed"))


```


```{r}

```






















```{r}
ggsave()
```


