---
title: "Mapping the big movers"
aauthor: "Ben Cresswell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
 html_document:
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 4
    fig_width: 4
    highlight: textmate
    theme: spacelab
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: inline
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = '', fig.width = 7, fig.height = 7)
options(knitr.duplicate.label = 'allow')
#rm(list=ls())
#getwd()
```


Note: Need to run the tidyeda.Rmd first to subset the required objects

# Load required packages
```{r packages, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(sp)
library(rgdal)
library(rgeos)
library(adehabitatHR)
library(leaflet)
library(cowplot)
library(ggmap)    # for fortifying shapefiles
library(ggsn) # Package with built in scale bar and north point
library(readxl)
library(scatterpie)
library(collapse)
library(tidyverse)
library(rayshader)
```

# First need a base map for QlD coast, GBR and CSMP

## Load world map object from ggplot
```{r world-map-load}
world <- map_data("world")
```

## Plot the map trimmed down to just GBR and Coral Sea area
```{r}
base_map <- 
  world %>% 
  filter(region == 'Australia') %>% 
  ggplot() +
  geom_polygon(aes(x = long, y = lat, group = group), colour = 'grey10', fill = 'grey40', lwd = 0.3) +
  coord_map(ylim = c(-24, -10), xlim = c(143, 152.8)) 
base_map
```


Looking about right. Get reefs on it.

## Load in shape files from 3dgbr using ggmap
```{r shape-files-load, message=FALSE, warning=FALSE}
cs_dryreef <- readOGR("../data/3dgbr_geomorph/shape", "coralsea_dryreef")
cs_reef <- readOGR("../data/3dgbr_geomorph/shape", "coralsea_reef")
#cs_cays <- readOGR("../data/3dgbr_geomorph/shape", "coralsea_cay")
#gbr_dryreef <- readOGR("../data/3dgbr_geomorph/shape", "gbr_dryreef")
#gbr_feats <- readOGR("../data/3dgbr_geomorph/shape", "gbr_features")
#gbr_shelf <- readOGR("../data/3dgbr_geomorph/shape", "gbr_shelf")
```

## These can't be plotted directly in ggplot so need to be converted to dataframes:
```{r message=FALSE}
cs_dryreef_df <- fortify(cs_dryreef)
cs_reef_df <- fortify(cs_reef)
#cs_cays_df <- fortify(cs_cays)
#gbr_dryreef_df <- fortify(gbr_dryreef)
#gbr_feats_df <- fortify(gbr_feats)
#gbr_shelf_df <- fortify(gbr_shelf)
```


# Now the shapefile can be plotted as either a geom_path or a geom_polygon.
```{r}
reefsmap<- 
  base_map +
    #geom_path(data = gbr_dryreef_df, aes(x = long, y = lat, group = group), color = 'gray', size = .5) +
    #geom_polygon(data = gbr_feats_df, aes(x = long, y = lat, group = group), colour = 'grey10', fill = 'grey40', size = .02) +
    #geom_path(data = gbr_shelf_df, aes(x = long, y = lat, group = group), color = 'gray', fill = 'white', size = .2) +
    geom_polygon(data = cs_reef_df, aes(x = long, y = lat, group = group), color = 'gray', fill = 'gray', size = .2) + # Can use fill = on polygon but not path
    #geom_path(data = cs_cays_df, aes(x = long, y = lat, group = group), color = 'gray', fill = 'white', size = .2) +
    #geom_path(data = cs_dryreef_df, aes(x = long, y = lat, group = group), color = 'gray', size = .2) +
    theme(axis.title = element_blank(), 
        #axis.text = element_blank(),
        #axis.ticks = element_blank(),
        #panel.grid = element_line(colour = "#ECEFF1"),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent", colour = "transparent")) 

reefsmap
```


# Map tagging locations (need to run the wrangling script first to create the tag_locs object)

```{r}
source(knitr::purl("wrangling_bigmovers.Rmd", quiet=TRUE))
```


Also need to allocated some better labels/IDs to replace transmitter_id 

```{r}
tag_locs <- 
  tag_locs %>% 
  mutate(shark_id = case_when(grepl('4172', transmitter_id) ~ 'Tiger 1',
                              grepl('63847', transmitter_id) ~ 'Tiger 2',
                              grepl('63947', transmitter_id) ~ 'Tiger 3',
                              grepl('64080', transmitter_id) ~ 'Silver 1',
                              grepl('60580', transmitter_id) ~ 'Silver 2',
                              grepl('64103', transmitter_id) ~ 'Grey 1'))
```

```{r tagging-map}
taggingmap <- 
reefsmap +
geom_point(data = tag_locs, aes(x = Long, y = Lat, shape = Scientific_name, fill = shark_id), size = 4, position = position_nudge(x = -0.1, y = -0.2)) +
  scale_shape_manual(name = 'Shark ID', values = c(21, 22, 24)) +
  scale_fill_brewer(name = 'Shark ID', palette = "Dark2", direction = -1) +
  guides(fill = guide_legend(override.aes = list(shape = 21)),
         shape = 'none') +
  theme(legend.position = 'none') +
  theme(axis.title = element_blank(), 
        axis.text = element_blank(),
        axis.ticks = element_blank())
taggingmap

ggsave(taggingmap, filename = '../output/tagmap_bigsharks.png', width = 62, height = 100, units = 'mm', dpi = 400)
```

Circles are silvertips
Squares are greys
Triangles are tigers

# Plot legend separately
```{r}
library(ggpubr)
# Extract the legend. Returns a gtable
leg <- ggpubr::get_legend(taggingmap)

# Convert to a ggplot and print
shark_leg <- as_ggplot(leg)

ggsave(shark_leg, filename = '../output/sharklegend.png', width = 62, height = 100, units = 'mm', dpi = 400)
```



# Now need to plot the movement segments/arrows/curves on this
- Going to use the Dark2 palette from RColourBrewer as it has enough options. 
- If we need more than 8 will have to turn to 'Paired' or look at custom options.
```{r}
library(RColorBrewer)
display.brewer.all(colorblindFriendly = TRUE)
```

# As a curve - all from mover_sum_location
```{r}
#movement_map1 <-
  reefsmap +
  geom_curve(data = mover_sum_location, aes(x = From_Long, y = From_Lat, xend = To_Long, yend = To_Lat, colour = transmitter_id),
             size = 1, angle = 90, curvature = 0.4, arrow = arrow(length = unit(0.3, "cm"), type="closed")) +
  #scale_fill_manual(values = wes_palette("GrandBudapest1")) +
  #scale_colour_viridis_d()+
  scale_colour_brewer(palette = "Dark2")+
  #geom_point(data = tag_locs, aes(x = Long, y = Lat, shape = Scientific_name, fill = transmitter_id), size = 4, position = position_nudge(x = -0.1, y = -0.2)) +
  #scale_shape_manual(values = c(21, 22, 24)) +
  coord_quickmap(ylim = c(-24, -10), xlim = c(143, 152.8))  # geom_curve doesn't play nicely with coord_map 


```

Because some individuals have made the same movements they are masked in this plot - will need to split out the mover_sum_reef df and plot tigers separate from GRS and silvers - then set curvature and angle separately.
Also want to make a more meaningful legend...


```{r}
tiger_locmovs <- 
  tiger_locmovs %>% 
  mutate(shark_id = case_when(grepl('4172', transmitter_id) ~ 'Tiger 1',
                              grepl('63847', transmitter_id) ~ 'Tiger 2',
                              grepl('63947', transmitter_id) ~ 'Tiger 3'))
  
  
other_locmovs <- 
  other_locmovs %>% 
  mutate(shark_id = case_when(grepl('64080', transmitter_id) ~ 'Silver 1',
                              grepl('60580', transmitter_id) ~ 'Silver 2',
                              grepl('64103', transmitter_id) ~ 'Grey 1'))

```




# As a curve - separate
```{r message=FALSE, warning=FALSE}
bigmov_map <- 
  reefsmap +
  geom_curve(data = tiger_locmovs, aes(x = From_Long, y = From_Lat, xend = To_Long, yend = To_Lat, colour = transmitter_id),
          lty = "11", size = 1, angle = 90, curvature = 0.25 , arrow = arrow(length = unit(0.3, "cm"), type="closed")) +
  geom_curve(data = other_locmovs, aes(x = From_Long, y = From_Lat, xend = To_Long, yend = To_Lat, colour = transmitter_id),
          lty = "solid",  size = 1, angle = 120, curvature = 0.5, arrow = arrow(length = unit(0.3, "cm"), type="closed")) +
  scale_colour_brewer(palette = "Dark2", direction = -1) +
  #scale_colour_viridis_d() +                                                                                                              # viridis colour option
  guides(fill = 'none', colour = 'none') +
  labs(colour = "Individual ID") +
  theme(legend.text = element_text(face = "italic"),
        legend.position = c(.8,.8)) +
  geom_rect(aes(xmin = 147.5, xmax = 149, ymin = -18.2, ymax = -16.1), color="grey50", fill = 'transparent')+
  coord_quickmap(ylim = c(-24, -10), xlim = c(143, 158))  # geom_curve doesn't play nicely with coord_map 
bigmov_map
ggsave(bigmov_map, filename = '../output/bigmove_map.png', width = 200, height = 200, units = 'mm', dpi = 400)
```



```{r}
#ggsave(bigmov_map, filename = '../output/movement_mapV2.png', width = 200, height = 200, units = 'mm', dpi = 400)
```




## Zoomed-in map for insetting

### Could just crop the map above
```{r}
#zoom_map <- 
  bigmov_map +
  coord_quickmap(ylim = c(-18.2, -16.1), xlim = c(147.5, 149)) # geom_curve doesn't play nicely with coord_map 
```
A few issues though and it would be nice to have different curvatures for the segments on this map


### Work up from scratch
```{r bigmov-zoom-map, fig.width = 4, fig.height = 7}
zoom_map <- 
  reefsmap +
  geom_curve(data = tiger_sublocmovs, aes(x = From_Long, y = From_Lat, xend = To_Long, yend = To_Lat, colour = transmitter_id),
             lty = "11", size = 1, size = 1, angle = 120, curvature = 0.35, arrow = arrow(length = unit(0.3, "cm"), type="closed")) +
  geom_curve(data = other_sublocmovs, aes(x = From_Long, y = From_Lat, xend = To_Long, yend = To_Lat, colour = transmitter_id),
             lty = "solid",  size = 1, size = 1, angle = 90, curvature = 0.55, arrow = arrow(length = unit(0.3, "cm"), type="closed")) +
  scale_colour_brewer(palette = "Dark2", direction = -1) +
  #scale_colour_viridis_d() +                                                        # viridis colour option
  guides(colour = 'none', fill = 'none', shape = 'none') +                           # Don't want any legend
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        panel.background = element_rect(fill = "white"),
        plot.background = element_rect(fill = "transparent", colour = "transparent")) +
  coord_quickmap(ylim = c(-18.2, -16.1), xlim = c(147.5, 149)) # geom_curve doesn't play nicely with coord_map 
  
zoom_map
```


# Save if required
```{r}
ggsave(zoom_map, filename = "../output/bigmove-zoomed.jpg", width = 62, height = 100, units = 'mm')
```

```{r}
bigmov_zoom <- 
  bigmov_map + annotation_custom(
    ggplotGrob(zoom_map), 
    xmin = 151, xmax = 159.5, ymin = -24, ymax = -15)
bigmov_zoom
ggsave(bigmov_zoom, filename = "../output/bigmove-zoom.jpg", width = 200, height = 200, units = 'mm')
```

## Zoom inset explanation:
A69-9001-63847	Galeocerdo cuvier	            2021-03-16	Capricorn Bunkers	->  Holmes - West     |	2021-07-13	Holmes - West	   -> Flinders - North
A69-9001-64080	Carcharhinus albimarginatus	  2021-02-22  Holmes - West	    ->  Flinders - North  | 2021-03-25	Flinders - North ->	Osprey	
A69-9001-60580	Carcharhinus amblyrhynchos	  2021-10-24  Flinders - South  ->	Holmes - East	
A69-9001-63947	Galeocerdo cuvier           	2021-08-10	Palm Islands      ->	Flinders - North



# Create Australia overview map for inset
```{r}
straya <- 
  world %>% 
  filter(region == 'Australia') %>% 
  ggplot() +
  geom_polygon(aes(x = long, y = lat, group = group), colour = 'black', fill = 'grey20', lwd = 0.3) +
  theme(axis.title = element_blank(), 
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_line(colour = "transparent"),
        #panel.border = element_rect(colour = "black", fill = "transparent"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent", colour = "transparent")) +
  geom_rect(aes(xmin = 143, xmax = 153, ymin = -24, ymax = -10), color = "white", fill = 'transparent', lwd = 0.01) +
  coord_quickmap(ylim = c(-45, -8), xlim = c(112, 154)) 
straya
```



# Add overview map, scale bar and N pointer
```{r}
bigmov_final <- 
  bigmov_zoom +
  annotation_custom(ggplotGrob(straya), xmin = 141, xmax = 148, ymin = -24.5, ymax = -21) +
  scalebar(cs_dryreef_df, dist = 200, dist_unit = "km", transform = TRUE, model = "WGS84", height = 0.008, 
           location = 'bottomright', anchor = c(x = 157, y = -24.4), family = "Arial", st.size = 3.2, border.size = 0.4, st.bottom = FALSE) +
  draw_image('../data/North_Pointer.jpg', x = 144.2, y = -21, scale = 1.5)
bigmov_final
ggsave(bigmov_final, filename = "../output/bigmover_fig_final.jpg", width = 200, height = 200, units = 'mm')

```




## PLOTTING WITH ALL ELEMENTS SEPARATELY ##

```{r message=FALSE, warning=FALSE}
bigmov_map2 <- 
  reefsmap +
  geom_curve(data = tiger_locmovs, aes(x = From_Long, y = From_Lat, xend = To_Long, yend = To_Lat, colour = transmitter_id),
          lty = "11", size = 1, angle = 90, curvature = 0.25 , arrow = arrow(length = unit(0.3, "cm"), type="closed")) +
  geom_curve(data = other_locmovs, aes(x = From_Long, y = From_Lat, xend = To_Long, yend = To_Lat, colour = transmitter_id),
          lty = "solid",  size = 1, angle = 120, curvature = 0.5, arrow = arrow(length = unit(0.3, "cm"), type="closed")) +
  scale_colour_brewer(palette = "Dark2", direction = -1) +
  #scale_colour_viridis_d() +                                                                                                              # viridis colour option
  guides(fill = 'none', colour = 'none') +
  labs(colour = "Individual ID") +
  theme(legend.text = element_text(face = "italic"),
        legend.position = c(.8,.8)) +
  geom_rect(aes(xmin = 147.5, xmax = 149, ymin = -18.2, ymax = -16.1), color="grey50", fill = 'transparent')+
  coord_quickmap(ylim = c(-24, -10), xlim = c(143, 154)) +  # geom_curve doesn't play nicely with coord_map 
  annotation_custom(ggplotGrob(straya), xmin = 141, xmax = 148, ymin = -24.5, ymax = -21) +
  scalebar(cs_dryreef_df, dist = 200, dist_unit = "km", transform = TRUE, model = "WGS84", height = 0.008, 
           location = 'bottomright', anchor = c(x = 150.2, y = -24.2), family = "Arial", st.size = 3.2, border.size = 0.4, st.bottom = FALSE) +
  draw_image('../data/North_Pointer.jpg', x = 144.2, y = -21, scale = 1.5)
bigmov_map2
ggsave(bigmov_map2, filename = '../output/bigmove_map2.png', width = 125, height = 200, units = 'mm', dpi = 400)

```








### MAPPING ARCHIVE CODE ###

```{r}





reefsmap +
  geom_curve(data = mover_sum_sublocation, aes(x = From_Long, y = From_Lat, xend = To_Long, yend = To_Lat, colour = transmitter_id),
             size = 1, angle = 100, curvature = 0.3, arrow = arrow(length = unit(0.3, "cm"), type="closed")) +
  geom_point(data = tag_locs, aes(x = Long, y = Lat, shape = Scientific_name, fill = transmitter_id), size = 4) +
  scale_shape_manual(values = c(21, 22, 24)) +
  guides(colour = 'none', fill = 'none', shape = 'none') +                           # Don't want any legend
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        panel.background = element_rect(fill = "white"),
        plot.background = element_rect(fill = "transparent", colour = "transparent")) +
  coord_quickmap(ylim = c(-18.2, -16.1), xlim = c(147.5, 149)) # geom_curve doesn't play nicely with coord_map 

```



