---
title: "Mapping Ri"
aauthor: "Ben Cresswell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
 html_document:
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 4
    fig_width: 4
    highlight: textmate
    theme: spacelab
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: inline
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = '', fig.width = 6, fig.height = 3.75)
options(knitr.duplicate.label = 'allow')
#rm(list=ls())
#getwd()
```

# Load required packages
```{r packages, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(sp)
library(rgdal)
library(rgeos)
library(adehabitatHR)
library(leaflet)
library(cowplot)
library(ggmap)    # for fortifying shapefiles
library(ggsn) # Package with built in scale bar and north point
library(readxl)
library(scatterpie)
library(collapse)
library(tidyverse)
library(rayshader)
```

# First need a base map object(s)
```{r}
world <- map_data("world")
straya <- world %>% 
  filter(region == 'Australia')
```



If you want the object world for plotting down the line..


## Load in shape files for reefs and fortify
```{r shape-files-load, message=FALSE, warning=FALSE, include=FALSE}

# Coral Sea shape files
cs_dryreef_df <- readOGR("../data/3dgbr_geomorph/shape", "coralsea_dryreef") %>% fortify # Don't need dry reef file
cs_reef_df <- readOGR("../data/3dgbr_geomorph/shape", "coralsea_reef") %>% fortify # Can make fillable polygons with this df
#cs_cays_df <- readOGR("../data/3dgbr_geomorph/shape", "coralsea_cay") %>% fortify # Don't need the cays for this scale of mapping

# GBR
#gbr_dryreef_df <- readOGR("../data/3dgbr_geomorph/shape", "gbr_dryreef") %>% fortify # gbr_dryreef is too big and just duplicates the feats file
gbr_feats_df <- readOGR("../data/3dgbr_geomorph/shape", "gbr_features") %>% fortify # Outlines of main reefs
gbr_shelf_df <- readOGR("../data/3dgbr_geomorph/shape", "gbr_shelf") %>% fortify # Includes inshore detail (so can use to map coastline better than straya object)

# Park boundaries - don't need for this as we are so zoomed in they aren't captured
#csmp_df <- readOGR("../data/3dgbr_geomorph/shape", "qld_gbrwha_cscz") %>% fortify
#gbr_df <- readOGR("../data/3dgbr_geomorph/shape", "gbrwha_outer") %>% fortify
```

# Shape file adjustments
For plotting Ri, we are only interested in the 4 reefs where we tagged organisms/had the array deployed and not the ones outside of this.
Would be good to shrink the gbr feats object a bit but it doesn't work
```{r}
#cs_dryreef_df <-  cs_dryreef_df %>% filter(long <149) # Not relevant. Also if plotting eastern reefs, the dry reefs layer is best
cs_reef_df <- cs_reef_df %>% filter(long <149)
straya <- world %>% filter(region == 'Australia') %>% filter(lat >-18)

```


# Pull in Ri
Sharks and f
```{r run-wrangle, message=FALSE, warning=FALSE, include=FALSE}
source(knitr::purl("ri_sharks.Rmd", quiet=TRUE))
```

# Additional plotting variables
## Grey reef sharks
```{r}
# Assign reef location
grs_installation_stats <- 
grs_installation_stats %>% 
  mutate(lat = case_when(grepl("Osprey", installation_name) ~ -13.88,
                       grepl("Bougain", installation_name) ~ -15.5,
                       grepl("Holmes", installation_name) ~ -16.48,
                       grepl("Flind", installation_name) ~ -17.58),
       long = case_when(grepl("Osprey", installation_name) ~ 146.60,
                        grepl("Bougain", installation_name) ~ 147.1,
                        grepl("Holmes", installation_name) ~ 147.98,
                        grepl("Flind", installation_name) ~ 148.45))

# Assign label location
grs_installation_stats <- 
grs_installation_stats %>% 
mutate(label_lat = case_when(grepl("Osprey", installation_name) ~ -14.5,
                        grepl("Bougain", installation_name) ~ -15.5,
                        grepl("Holmes", installation_name) ~ -16.5,
                        grepl("Flind", installation_name) ~ -17.5),
       label_long = case_when(grepl("Osprey", installation_name) ~ 149,
                         grepl("Bougain", installation_name) ~ 149,
                         grepl("Holmes", installation_name) ~ 149,
                         grepl("Flind", installation_name) ~ 149))


# Assign bubble position
grs_installation_stats <- 
grs_installation_stats %>% 
mutate(lat1 = case_when(grepl("Osprey", installation_name) ~ -14.5,
                        grepl("Bougain", installation_name) ~ -15.5,
                        grepl("Holmes", installation_name) ~ -16.5,
                        grepl("Flind", installation_name) ~ -17.5),
       long1 = case_when(grepl("Osprey", installation_name) ~ 150.5,
                         grepl("Bougain", installation_name) ~ 150.5,
                         grepl("Holmes", installation_name) ~ 150.5,
                         grepl("Flind", installation_name) ~ 150.5))
grs_installation_stats
```





## Silver tip sharks
```{r}
# Assign reef location
silvers_installation_stats <- 
  silvers_installation_stats %>% 
  mutate(lat = case_when(grepl("Osprey", installation_name) ~ -13.88,
                         grepl("Bougain", installation_name) ~ -15.5,
                         grepl("Holmes", installation_name) ~ -16.48,
                         grepl("Flind", installation_name) ~ -17.58),
         long = case_when(grepl("Osprey", installation_name) ~ 146.60,
                          grepl("Bougain", installation_name) ~ 147.1,
                          grepl("Holmes", installation_name) ~ 147.98,
                          grepl("Flind", installation_name) ~ 148.45))

# Assign label location
silvers_installation_stats <- 
  silvers_installation_stats %>% 
  mutate(label_lat = case_when(grepl("Osprey", installation_name) ~ -14.5,
                               grepl("Bougain", installation_name) ~ -15.5,
                               grepl("Holmes", installation_name) ~ -16.5,
                               grepl("Flind", installation_name) ~ -17.5),
         label_long = case_when(grepl("Osprey", installation_name) ~ 149,
                                grepl("Bougain", installation_name) ~ 149,
                                grepl("Holmes", installation_name) ~ 149,
                                grepl("Flind", installation_name) ~ 149))


# Assign bubble position
silvers_installation_stats <- 
  silvers_installation_stats %>% 
  mutate(lat1 = case_when(grepl("Osprey", installation_name) ~ -14.5,
                          grepl("Bougain", installation_name) ~ -15.5,
                          grepl("Holmes", installation_name) ~ -16.5,
                          grepl("Flind", installation_name) ~ -17.5),
         long1 = case_when(grepl("Osprey", installation_name) ~ 151.5,
                           grepl("Bougain", installation_name) ~ 151.5,
                           grepl("Holmes", installation_name) ~ 151.5,
                           grepl("Flind", installation_name) ~ 151.5))
silvers_installation_stats



```


# Basemap
```{r}
ri_basemap <- ggplot() +
  geom_path(data = gbr_shelf_df, aes(x = long, y = lat, group = group), color = 'grey20', size = .2) +
  geom_polygon(data = gbr_feats_df, aes(x = long, y = lat, group = group), fill = 'grey50', size = .1) +
  geom_polygon(data = gbr_shelf_df, aes(x = long, y = lat, group = group), fill = 'grey90', size = .1,  alpha = .4) +
  geom_path(data = gbr_feats_df, aes(x = long, y = lat, group = group), color = 'grey20', size = .1) +
  geom_polygon(data = cs_reef_df, aes(x = long, y = lat, group = group), color = 'black', fill = 'gray75', size = .2) + 
  theme(axis.title = element_blank(), 
        #axis.text = element_blank(),
        #axis.ticks = element_blank(),
        #panel.grid = element_line(colour = "#ECEFF1"),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent", colour = "transparent")) +
  coord_map(ylim = c(-18, -13.5), xlim = c(145.5, 149))

ri_basemap
```



```{r}
ri_map <- 
ri_basemap +
  geom_segment(data = grs_installation_stats, aes(x = long, y = lat, xend = label_long-0.1, yend = label_lat), size = .3,  col = "grey60") +
  geom_polygon(data = cs_reef_df, aes(x = long, y = lat, group = group), color = 'black', fill = 'gray75', size = .2) +
  geom_point(data = grs_installation_stats, aes(x = long1-1.4, y = lat1, size = mean, fill = installation_name), stroke = 0.5, pch = 21) +
  #geom_label(data = grs_installation_stats, aes(x = label_long , y = label_lat, label = installation_name), fill = "white") +
  geom_point(data = silvers_installation_stats, aes(x = long1-1.3, y = lat1, size = mean, fill = installation_name), stroke = 0.5, pch = 21) +
  scale_size(range = c(6.5, 41)) +
  scale_shape_manual(name = 'Reef') +
  scale_fill_manual(values =  installation_palette) +
  geom_text(data = grs_installation_stats, aes(x = long1, y = lat1, label = mean)) +
  geom_text(data = silvers_installation_stats, aes(x = long1, y = lat1, label = mean)) +
  theme(legend.position = 'none')

#ggsave("../output/ri_map.png", plot = ri_map, width = 220, height = 138, units = "mm")

ri_map

```




