---
title: "Base map for individual reefs"
aauthor: "Ben Cresswell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
 html_document:
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    highlight: textmate
    theme: spacelab
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: inline
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      #fig.width = 4.8, fig.height = 3
                      fig.width = 12, fig.height = 8
                      )
options(knitr.duplicate.label = 'allow')
#rm(list=ls())
getwd()
```


# Load required packages
```{r packages, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(sp)
library(rgdal)
library(rgeos)
library(adehabitatHR)
library(leaflet)
library(cowplot)
library(ggmap)    # for fortifying shapefiles
library(ggsn)
library(patchwork)
library(readxl)
library(scatterpie)
library(collapse)
library(tidyverse)
```


# Part A. Wrangle in data

## 1. Osprey reef area data:
```{r read-osprey-data, message=FALSE, warning=FALSE, include=FALSE}
osprey_reef <- readOGR("../data/3dgbr_geomorph/shape", "coralsea_reef") %>% fortify() %>% filter(long < 147) %>% filter(lat > -14.1)
osprey_dryreef <- readOGR("../data/3dgbr_geomorph/shape", "coralsea_dryreef") %>% fortify() %>% filter(long < 147) %>% filter(lat > -14.1)
```

## 2. Receiver stations
```{r read-station-data, message=FALSE, warning=FALSE, include=FALSE}
stations <- read_excel("../data/receiver_list_dep1.xlsx") %>% 
  mutate_if(is.character, as.factor) %>% 
  mutate(label_long = 146.52, label_lat = station_latitude*1.001) %>%       ## Separate locations for placing labels 
  mutate(station_name = str_sub(station_name, 4, -1))                  ## Or can plot text within circles (points)
#stations
```

## 3. Teleost Ri
```{r run-wrangle, message=FALSE, warning=FALSE, include=FALSE}
source(knitr::purl("ri_teleosts.Rmd", quiet=TRUE))
```


# Part B. Plots






```{r osprey-main-fig}
osprey_main<- 
  ggplot() +
  geom_point(data = project_serials_teleosts, aes(x = Long, y =Lat), colour = 'black', fill = 'red', size = 4,  stroke = 0.5, shape = 23 ) +    # Tagging locations
  geom_polygon(data = osprey_reef, aes(x = long, y = lat, group = group), color = 'grey30', fill = 'dodgerblue', alpha = 0.5, lwd = 0.3) +
  geom_polygon(data = osprey_dryreef, aes(x = long, y = lat, group = group), color = 'grey10', fill = 'seagreen', lwd = 0.3) +
  geom_point(data = stations, aes(x = station_longitude, y =station_latitude), colour = 'black', fill = 'navyblue', size = 6,  stroke = 0.5, shape = 21 ) +
  geom_text(data = stations, aes(x = station_longitude, y =station_latitude, label = station_name), colour = "white", size = 3) +
  theme(axis.title = element_blank(), 
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        #axis.ticks = element_blank(),
        #panel.grid = element_line(colour = "#ECEFF1"),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent", colour = "transparent")) +
  coord_quickmap(ylim = c(-13.97, -13.75), xlim = c(146.42, 146.65))
```


```{r}
ggsave("../output/osprey_main.png", plot = osprey_main, width = 220, units = "mm", dpi = 300)

```

```{r}
#osprey_final_nobars <- 
  osprey_main +
   scalebar(osprey_reef, dist = 2.5, dist_unit = "km", transform = TRUE, model = "WGS84",            # Geo properties
           location = 'bottomright', anchor = c(x = 146.65, y = -13.977),                                # Position of bar
           family = "Arial", st.size = 4, st.dist = 0.0015,                                            # Text properties
           height = 0.0005, border.size = 0.5, st.bottom = FALSE) +
    draw_image('../data/North_Pointer.jpg', x = 146.64, y = -13.76, hjust = 0.5, vjust = 0.5, scale = 0.025)

```


```{r}
ggsave("../output/osprey_main_scale.png", plot = osprey_final_nobars, width = 220, units = "mm", dpi = 300)

```

```{r}
station_ri_stats_gts
station_ri_stats_lugub
```



## Struggling to get the two teleost stats dfs to full join and complete missing values (Lugubs have no obs at O4 or O5)
### HACK
```{r}
station_ri_stats_lugub <- 
station_ri_stats_lugub %>% 
  merge(station_ri_stats_gts[c(2,3)], all = TRUE) %>% 
  mutate(Scientific_name = replace_na(Scientific_name, "Caranx lugubris"))


```





```{r}
station_ri_stats_teleosts <- 
  station_ri_stats_gts %>% 
  bind_rows(station_ri_stats_lugub) #

write.csv(station_ri_stats_teleosts, "../output/teleost_station_ri.csv")

```



# Bar plots

# North Horn - CS-O1
```{r}
CS_01 <- 
station_ri_stats_teleosts %>% 
  filter(station_name_long == "North_Horn") %>% 
  ggplot(aes(x = Scientific_name, y = mean, fill = Scientific_name)) +
  geom_bar(stat="identity", position="dodge", color="black", width = 0.95) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9)) +
  scale_x_discrete(labels = NULL, expand = expansion(add=c(1,0.6)))+
  scale_fill_manual(values = c("grey85", "grey25"))  +
  scale_y_continuous(expand = c(0,0), limits = c(0,0.12), breaks = c(0.1)) +
  ggtitle("North Horn") +
  theme(panel.grid = element_line(colour = "#ECEFF1"),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        axis.ticks.length.y = unit(c(.0, -.15), "cm"),
        axis.ticks.x = element_blank(),
        axis.text.y = element_text(size = 10, colour = "black", margin = margin(l = 10, r = -20)), 
        axis.text.x = element_blank(),
        axis.title = element_blank(),
        plot.title = element_text(size = 10),
        panel.background = element_rect(fill = "white", colour = "black"),
        plot.background = element_rect(fill = "transparent", colour = "transparent"),
        legend.position = "none") 


CS_01
```


```{r}
ggsave("../output/osprey_O1.png", plot = CS_01, height = 30, width = 48, units = "mm", dpi = 300)
```




# Silver City (O2)
```{r}
CS_02 <- 
station_ri_stats_teleosts %>% 
  filter(station_name_long == "Silver_City") %>% 
  ggplot(aes(x = Scientific_name, y = mean, fill = Scientific_name)) +
  geom_bar(stat="identity", position="dodge", color="black", width = 0.95) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9)) +
  scale_x_discrete(labels = NULL, expand = expansion(add=c(1,0.6)))+
  scale_fill_manual(values = c("grey85", "grey25"))  +
  scale_y_continuous(expand = c(0,0), limits = c(0,0.24), breaks = c(0.1, 0.2)) +
  ggtitle("Silver City") +
  theme(panel.grid = element_line(colour = "#ECEFF1"),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        axis.ticks.length.y = unit(c(.0, -.15), "cm"),
        axis.ticks.x = element_blank(),
        axis.text.y = element_text(size = 10, colour = "black", margin = margin(l = 10, r = -20)), 
        axis.text.x = element_blank(),
        axis.title = element_blank(),
        plot.title = element_text(size = 10),
        panel.background = element_rect(fill = "white", colour = "black"),
        plot.background = element_rect(fill = "transparent", colour = "transparent"),
        legend.position = "none") 
CS_02
```




```{r}
ggsave("../output/osprey_O2.png", plot = CS_02, height = 30, width = 48, units = "mm", dpi = 300)
```


# Overnight_Mooring (O3)
```{r}
CS_03 <- 
station_ri_stats_teleosts %>% 
  filter(station_name_long == "Overnight_Mooring") %>% 
  ggplot(aes(x = Scientific_name, y = mean, fill = Scientific_name)) +
  geom_bar(stat="identity", position="dodge", color="black", width = 0.95) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9)) +
  scale_x_discrete(labels = NULL, expand = expansion(add=c(1,0.6)))+
  scale_fill_manual(values = c("grey85", "grey25"))  +
  scale_y_continuous(expand = c(0,0), limits = c(0,0.72), breaks = c(0.2, 0.4, 0.6)) +
  ggtitle("Overnight Mooring") +
  theme(panel.grid = element_line(colour = "#ECEFF1"),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        axis.ticks.length.y = unit(c(.0, -.15), "cm"),
        axis.ticks.x = element_blank(),
        axis.text.y = element_text(size = 10, colour = "black", margin = margin(l = 10, r = -20)), 
        axis.text.x = element_blank(),
        axis.title = element_blank(),
        plot.title = element_text(size = 10),
        panel.background = element_rect(fill = "white", colour = "black"),
        plot.background = element_rect(fill = "transparent", colour = "transparent"),
        legend.position = "none") 
CS_03
```

```{r}
ggsave("../output/osprey_O3.png", plot = CS_03, height = 30, width = 48, units = "mm", dpi = 300)
```


# Lagoon_1 (O4)
```{r}
CS_04 <- 
station_ri_stats_teleosts %>% 
  filter(station_name_long == "Lagoon_1") %>% 
  ggplot(aes(x = Scientific_name, y = mean, fill = Scientific_name)) +
  geom_bar(stat="identity", position="dodge", color="black", width = 0.95) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9)) +
  scale_x_discrete(labels = NULL, expand = expansion(add=c(1,0.6)))+
  scale_fill_manual(values = c("grey85", "grey25"))  +
  scale_y_continuous(expand = c(0,0), limits = c(0,0.48), breaks = c(0.2, 0.4)) +
  ggtitle("Lagoon 1") +
  theme(panel.grid = element_line(colour = "#ECEFF1"),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        axis.ticks.length.y = unit(c(.0, -.15), "cm"),
        axis.ticks.x = element_blank(),
        axis.text.y = element_text(size = 10, colour = "black", margin = margin(l = 10, r = -20)), 
        axis.text.x = element_blank(),
        axis.title = element_blank(),
        plot.title = element_text(size = 10),
        panel.background = element_rect(fill = "white", colour = "black"),
        plot.background = element_rect(fill = "transparent", colour = "transparent"),
        legend.position = "none") 
CS_04
```

```{r}
ggsave("../output/osprey_O4.png", plot = CS_04, height = 30, width = 48, units = "mm", dpi = 300)
```



# Lagoon_2 (O5)
```{r}
CS_05 <- 
station_ri_stats_teleosts %>% 
  filter(station_name_long == "Lagoon_2") %>% 
  ggplot(aes(x = Scientific_name, y = mean, fill = Scientific_name)) +
  geom_bar(stat="identity", position="dodge", color="black", width = 0.95) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9)) +
  scale_x_discrete(labels = NULL, expand = expansion(add=c(1,0.6)))+
  scale_fill_manual(values = c("grey85", "grey25"))  +
  scale_y_continuous(expand = c(0,0), limits = c(0,0.12), breaks = c(0.1)) +
  ggtitle("Lagoon 2") +
  theme(panel.grid = element_line(colour = "#ECEFF1"),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        axis.ticks.length.y = unit(c(.0, -.15), "cm"),
        axis.ticks.x = element_blank(),
        axis.text.y = element_text(size = 10, colour = "black", margin = margin(l = 10, r = -20)), 
        axis.text.x = element_blank(),
        axis.title = element_blank(),
        plot.title = element_text(size = 10),
        panel.background = element_rect(fill = "white", colour = "black"),
        plot.background = element_rect(fill = "transparent", colour = "transparent"),
        legend.position = "none") 
CS_05
```

```{r}
ggsave("../output/osprey_O5.png", plot = CS_05, height = 30, width = 48, units = "mm", dpi = 300)
```





# Around_The_Bend (O6)
```{r}
CS_06 <- 
station_ri_stats_teleosts %>% 
  filter(station_name_long == "Around_The_Bend") %>% 
  ggplot(aes(x = Scientific_name, y = mean, fill = Scientific_name)) +
  geom_bar(stat="identity", position="dodge", color="black", width = 0.95) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9)) +
  scale_x_discrete(labels = NULL, expand = expansion(add=c(1,0.6)))+
  scale_fill_manual(values = c("grey85", "grey25"))  +
  scale_y_continuous(expand = c(0,0), limits = c(0,0.60), breaks = c(0.1, 0.3, 0.5)) +
  ggtitle("Around Bend") +
  theme(panel.grid = element_line(colour = "#ECEFF1"),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        axis.ticks.length.y = unit(c(.0, -.15), "cm"),
        axis.ticks.x = element_blank(),
        axis.text.y = element_text(size = 10, colour = "black", margin = margin(l = 10, r = -20)), 
        axis.text.x = element_blank(),
        axis.title = element_blank(),
        plot.title = element_text(size = 10),
        panel.background = element_rect(fill = "white", colour = "black"),
        plot.background = element_rect(fill = "transparent", colour = "transparent"),
        legend.position = "none") 
CS_06
```

```{r}
ggsave("../output/osprey_O6.png", plot = CS_06, height = 30, width = 48, units = "mm", dpi = 300)
```



# False_Entrance (O7)
```{r}
CS_07 <- 
station_ri_stats_teleosts %>% 
  filter(station_name_long == "False_Entrance") %>% 
  ggplot(aes(x = Scientific_name, y = mean, fill = Scientific_name)) +
  geom_bar(stat="identity", position="dodge", color="black", width = 0.95) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9)) +
  scale_x_discrete(labels = NULL, expand = expansion(add=c(1,0.6)))+
  scale_fill_manual(values = c("grey85", "grey25"))  +
  scale_y_continuous(expand = c(0,0), limits = c(0,0.12), breaks = c(0.1)) +
  ggtitle("False Entrance") +
  theme(panel.grid = element_line(colour = "#ECEFF1"),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        axis.ticks.length.y = unit(c(.0, -.15), "cm"),
        axis.ticks.x = element_blank(),
        axis.text.y = element_text(size = 10, colour = "black", margin = margin(l = 10, r = -20)), 
        axis.text.x = element_blank(),
        axis.title = element_blank(),
        plot.title = element_text(size = 10),
        panel.background = element_rect(fill = "white", colour = "black"),
        plot.background = element_rect(fill = "transparent", colour = "transparent"),
        legend.position = "none") 
CS_07
```


```{r}
ggsave("../output/osprey_O7.png", plot = CS_07, height = 30, width = 48, units = "mm", dpi = 300)
```


# Patchwork
```{r patch, fig.width=12, fig.height=8}
CS_01 + CS_02 + CS_03 +
  CS_04 + CS_05 + CS_06 + CS_07
```


# Extract legend


```{r}
### Make a dummy plot in ggplot
leg_plot <- 
  CS_07 +
  #scale_fill_manual(values=wes_palette(name="Moonrise3", n = 4, type = "discrete")) +
  #scale_shape_manual(name = '') +
  #scale_fill_manual(name = 'NULL', values =  installation_palette) +
  theme(legend.key = element_blank(),
        legend.background = element_rect(fill = "transparent"),
        legend.direction = "vertical",
        legend.title = element_blank(),
        legend.text = element_text(face = 'italic'),
        legend.position = "bottom")

### Plot legend separately using ggpubr
library(ggpubr)
legend <- 
  leg_plot %>% 
  get_legend() %>% 
  as_ggplot() +
  #annotate(geom = element_rect(size = 1, fill = "transparent")) #+
  theme(plot.background = element_rect(fill = "transparent", colour = "transparent"))

### Save
ggsave(legend, filename = '../output/teleostri_legend.png', width = 40, height = 64, units = 'mm', dpi = 300)
```




# Build up plot

```{r}
#osprey_ri_detail <- 
osprey_main +
   #geom_point(data = project_serials_teleosts, aes(x = Long, y =Lat), colour = 'black', fill = 'red', size = 4,  stroke = 0.5, shape = 23 ) +    # Tagging locations
   annotation_custom(ggplotGrob(CS_01), 
                    xmin = 146.49, xmax = 146.54, ymin = -13.80, ymax = -13.78) +   # ylim 0.1
   annotation_custom(ggplotGrob(CS_02), 
                    xmin = 146.5, xmax = 146.55, ymin = -13.86, ymax = -13.82) +     # ylim 0.2    
#   annotation_custom(ggplotGrob(CS_03), 
#                     xmin = 146.44, xmax = 146.49, ymin = -13.91, ymax = -13.81) +   # ylim 0.6
#   annotation_custom(ggplotGrob(CS_04), 
#                    xmin = 146.58, xmax = 146.63, ymin = -13.78, ymax = -13.75) +   # ylim 0.4
#   annotation_custom(ggplotGrob(CS_05), 
#                    xmin = 146.6, xmax = 146.65, ymin = -13.78, ymax = -13.75) +    # ylim 0.1
   annotation_custom(ggplotGrob(CS_06), 
                    xmin = 146.5, xmax = 146.55, ymin = -13.93, ymax = -13.86) +   # ylim 0.5
   annotation_custom(ggplotGrob(CS_07), 
                    xmin = 146.535, xmax = 146.585 , ymin = -13.965, ymax = -13.935)      # ylim 0.1

#osprey_ri_detail
```






```{r}

ggsave("../output/osprey_ri_detail.png", plot = osprey_ri_detail, width = 220, units = "mm", dpi = 300)


```







# Bubble plots
```{r}


station_ri_stats_teleosts %>% 
  filter(station_name_long == "North_Horn") %>% 
  ggplot(aes(x = Scientific_name, y = mean)) +
  geom_bar(stat="identity", position="dodge", color="black",fill = "steelblue", width = 0.95) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9)) +
  geom_point(aes(x = c(1, 2), y = c(0.4, 0.4), size = mean*100), stroke = 0.5, pch = 21) +
  scale_size(range = c(30, 600)) +
  #scale_x_discrete(labels = c("Silvers", "Greys"))+
 # scale_x_discrete(labels = NULL)+
  scale_y_continuous(expand = c(0,0), limits = c(0,0.7), breaks = c( 0.4, 0.6)) +
  theme(#panel.grid = element_line(colour = "#ECEFF1"),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        #axis.line = element_line(),
        panel.background = element_rect(fill = "white", colour = "black"),
        plot.background = element_rect(fill = "transparent", colour = "transparent"),
        legend.position = "bottom")  +
  labs(y= "", x = "")





```















# Overview map
```{r osprey-overview-map}
#osprey_overview <- 
  ggplot() +
  geom_polygon(data = osprey_reef, aes(x = long, y = lat, group = group), color = 'grey30', fill = 'grey80', lwd = 0.3) +
  geom_polygon(data = osprey_dryreef, aes(x = long, y = lat, group = group), color = 'grey10', fill = 'grey60', lwd = 0.3) +
  coord_quickmap(ylim = c(-14.1, -13.75), xlim = c(146.5, 146.75)) +
  theme(axis.title = element_blank(), 
        #axis.text = element_blank(),
        #axis.ticks = element_blank(),
        #panel.grid = element_line(colour = "#ECEFF1"),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent", colour = "transparent")) +
      draw_image('../data/North_Pointer.jpg', x = 146.65, y = -13.8, scale = 10000000)



#osprey_overview
```


# Test plot
```{r}




```




# Run whole script
```{r run-whole-script, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
#
```




