---
title: "Analysing Teleost Movement Timing and Distance - Ri"
author: "Ben Cresswell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
knit: (function(inputFile, encoding) { 
      out_dir <- "../output";
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), out_dir, 'teleost_movement_timingdistance_Ri.html')) })
output: 
 html_document:
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 6
    fig_width: 14
    highlight: textmate
    theme: spacelab
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: inline
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')
```


```{r packages, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# Packages
library(sp)
library(rgdal)
library(rgeos)
#library(tibbletime) # Time series management - don't think we need. lubridate prob better.
library(adehabitatHR)
library(leaflet)
library(ggmap)    # for fortifying shapefiles
library(readxl)
library(scatterpie)
library(plotrix)   # Calculates SE
library(collapse)
library(magrittr)
library(tidyverse)
```


```{r housekeeping, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# Housekeeping
#rm(list=ls())
#getwd()
```


# Data load and wrangling {.tabset .tabset-faded}

## Load data
### Going to load the main dataset and tease out movement time from there
```{r load-data, message=FALSE, warning=FALSE}
load(file = "../data/RData/alldata.RData")
```


# Select only variables and organisms required for this analysis

```{r}
diurnal_ri <- alldata %>%
  filter(Org_type != 'NA') %>%                        # We don't want the random detections included in this analysis
  filter(Scientific_name !='Galeocerdo cuvier') %>%   # Also don't want the visitors from outside the array included in this analysis  droplevels() %>% 
  dplyr::select(transmitter_id, 
                #receiver_name,                                                       # VR2W serial # - don't want this in
                detection_timestamp,                                                  # 
                installation_name, station_name, station_name_long,                   # Variables relating to detecting receiver
                #deploymentdatetime_timestamp, recoverydatetime_timestamp,            # Will add in deployment dates later (for whole proj, not individual deps)
                Common_name, Scientific_name, Date, 
                Location, Site, Sex, Org_type) %>%                                    # Leave in the orrganism and tagging info
  mutate(hour = hour(detection_timestamp)) %>% 
  mutate(tod = case_when(hour %in% (6:18) ~ "Day",
                         TRUE ~ "Night")) %>% 
  mutate(tag_date = as.Date(Date), 
         detection_date = as.Date(detection_timestamp),                               # One row/observation for every day the organism detected in array
         tag_loc = Location, 
         tag_site = Site, 
         .keep = 'unused') %>%
    dplyr::select(!hour) %>% 
  distinct
  
```



## Reload the latest receiver metadata file, if not already loaded (contains the VR2 retrieval dates)
```{r}
vr2ws_dep2 <- read_excel('../data/receiver_list_dep2.xlsx', trim_ws = TRUE) %>%
  tibble() %>% # Make into tibble format
  mutate(recovery_date = as.Date(recoverydatetime_timestamp), .keep = 'unused') %>% 
  mutate_if(is.character, as.factor) # Sort out variables
```

## Merge in just the retrieval dates to the main df
```{r}
diurnal_ri <- 
  diurnal_ri %>% 
  merge(vr2ws_dep2[c(4,10)], by='station_name') %>% 
  arrange(transmitter_id)
```

# Split out into day vs night
```{r}
day_ri <-
  diurnal_ri %>%
  filter(tod == 'Day') %>% 
  distinct()

night_ri <-
  diurnal_ri %>%
  filter(tod == 'Night') %>% 
  distinct()
```

# Calculate days at large and Ri by day vs night
## Day
```{r}
day_ri <- 
day_ri %>% 
  group_by(station_name, transmitter_id, tag_date) %>%
  mutate(detectiondays_station = n()) %>%
  #ungroup() %>%
  dplyr::select(!c(detection_date)) %>%
  distinct() %>%
  mutate(deploymentdays_station = as.integer(recovery_date - tag_date),
         ri_station = detectiondays_station/deploymentdays_station)
```

## Night
```{r}
night_ri <-
  night_ri %>% 
  group_by(station_name, transmitter_id, tag_date) %>%
  mutate(detectiondays_station = n()) %>%
  #ungroup() %>%
  dplyr::select(!c(detection_date)) %>%
  distinct() %>%
  mutate(deploymentdays_station = as.integer(recovery_date - tag_date),
         ri_station = detectiondays_station/deploymentdays_station)
```

# Bind back to one df
```{r}
daynight_ri <- 
  day_ri %>% 
  bind_rows(night_ri)
```


# Now filter out by taxa/organism type etc

## Teleost Ri day vs night - this is effectively installation Ri (presence vs absence over the whole of Osprey)
```{r}
teleost_ri_dn <- 
  daynight_ri %>% 
  filter(Org_type == "Teleost") %>% 
  group_by(tod) %>% 
  summarise(mean = mean(ri_station), sd = sd(ri_station), se = std.error(ri_station))
```

# GT Ri day vs night
```{r}
gt_ri_dn <- 
daynight_ri %>% 
  filter(Scientific_name == 'Caranx ignobilis') %>% 
  group_by(tod) %>% 
  summarise(mean = mean(ri_station), sd = sd(ri_station), se = std.error(ri_station))

gt_ri_dn %>% 
  ggplot(aes(x = tod, y = mean)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9)) +
  labs(y= "Ri", x = "Time of day")
```
Looking pretty even


# Black trevally Ri day vs night 
```{r}
lugub_ri_dn <- 
daynight_ri %>% 
  filter(Scientific_name == 'Caranx lugubris') %>% 
  group_by(tod) %>% 
  summarise(mean = mean(ri_station), sd = sd(ri_station), se = std.error(ri_station))

lugub_ri_dn %>% 
  ggplot(aes(x = tod, y = mean)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9)) +
  labs(y= "Ri", x = "Time of day")
```
Pretty similar - maybe more present in the day time

# Trout Ri day vs night - probably the most interesting
```{r}
trout_ri_dn <- 
daynight_ri %>% 
  filter(Common_name == "Footballer trout") %>% 
  group_by(tod) %>% 
  summarise(mean = mean(ri_station), sd = sd(ri_station), se = std.error(ri_station))

trout_ri_dn %>% 
  ggplot(aes(x = tod, y = mean)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9)) +
  labs(y= "Ri", x = "Time of day")
```
Note the small Ri for day time is caused by 2 observations at just after 6am.

# Can check by running:
```{r}
alldata %>%
  filter(Common_name == "Footballer trout") %>% 
  dplyr::select(transmitter_id, 
                #receiver_name,                                                       # VR2W serial # - don't want this in
                detection_timestamp,                                                  # 
                installation_name, station_name, station_name_long,                   # Variables relating to detecting receiver
                #deploymentdatetime_timestamp, recoverydatetime_timestamp,            # Will add in deployment dates later (for whole proj, not individual deps)
                Common_name, Scientific_name, Date, 
                Location, Site, Sex, Org_type) %>%                                    # Leave in the orrganism and tagging info
  mutate(hour = hour(detection_timestamp)) %>% 
  mutate(tod = case_when(hour %in% (6:18) ~ "Day",
                         TRUE ~ "Night")) %>% 
  filter(tod == "Day")
```


# What about diurnal Ri by station?

# GT Ri day vs night by station
```{r gt-dn-ri-plot, fig.width = 9}
gt_ri_dn_stn <- 
daynight_ri %>% 
  filter(Scientific_name == 'Caranx ignobilis') %>% 
  group_by(tod, station_name_long, station_name) %>% 
  summarise(mean = mean(ri_station), sd = sd(ri_station), se = std.error(ri_station))#

gt_ri_dn_plot <- 
gt_ri_dn_stn %>% 
  ggplot(aes(x = station_name, y = mean, fill = tod)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") +
  scale_fill_manual(values = c("white", "slateblue4")) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9)) +
  labs(y= "Ri", x = "Time of day") +
  theme(panel.grid = element_line(colour = "#ECEFF1"),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent", colour = "transparent")) +
  theme(legend.title = element_blank(),
        legend.position = c(.8,.8))

ggsave(gt_ri_dn_plot, filename = "../output/ri_dn_gt_bar.png", width = 160, height = 100, units = 'mm', dpi = 600)
```

# Black trevally Ri day vs night by station
```{r}
lugub_ri_dn_stn <- 
daynight_ri %>% 
  filter(Scientific_name == 'Caranx lugubris') %>% 
  group_by(tod, station_name_long, station_name) %>% 
  summarise(mean = mean(ri_station), sd = sd(ri_station), se = std.error(ri_station))

lugub_ri_dn_plot <- 
lugub_ri_dn_stn %>% 
  ggplot(aes(x = station_name, y = mean, fill = tod)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") +
  scale_fill_manual(values = c("white", "slateblue4")) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9)) +
  scale_y_continuous(expand = c(0,0), limits = c(-0.02,0.6), breaks = c(0, 0.2, 0.4, 0.6, 0.8)) +
  labs(y= "Ri", x = "Time of day") +
  theme(panel.grid = element_line(colour = "#ECEFF1"),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent", colour = "transparent")) +
  theme(legend.title = element_blank(),
        legend.position = c(.8,.8))

lugub_ri_dn_plot
ggsave(lugub_ri_dn_plot, filename = "../output/ri_dn_lugub_bar.png", width = 160, height = 100, units = 'mm', dpi = 600)
```
Pretty similar - maybe more present in the day time

# Trout Ri day vs night - probably the most interesting
```{r}
trout_ri_dn_stn <- 
daynight_ri %>% 
  filter(Common_name == "Footballer trout") %>% 
  group_by(tod, station_name_long, station_name) %>% 
  summarise(mean = mean(ri_station), sd = sd(ri_station), se = std.error(ri_station))

trout_ri_dn_plot <- 
trout_ri_dn_stn %>% 
  ggplot(aes(x = station_name, y = mean, fill = tod)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") +
  scale_fill_manual(values = c("white", "slateblue4")) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9)) +
  labs(y= "Ri", x = "Time of day") +
  theme(panel.grid = element_line(colour = "#ECEFF1"),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent", colour = "transparent")) +
  theme(legend.title = element_blank())

trout_ri_dn_plot
ggsave(trout_ri_dn_plot, filename = "../output/ri_dn_trout_bar.png", width = 160, height = 100, units = 'mm', dpi = 600)
```








