---
title: "Analysing residency indices - Sharks"
author: "Ben Cresswell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
knit: (function(inputFile, encoding) { 
      out_dir <- "../output";
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), out_dir, 'Ri_shark_analysis.html')) })
output: 
 html_document:
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 4
    fig_width: 4
    highlight: textmate
    theme: spacelab
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: inline
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r packages, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# Packages
library(knitr)
library(kableExtra)
library(sp)
library(rgdal)
library(rgeos)
library(adehabitatHR)
library(leaflet)
library(ggmap)    # for fortifying shapefiles
library(readxl)
library(scatterpie)
library(plotrix)   # Calculates SE
library(patchwork)
library(collapse)
library(magrittr)
library(tidyverse)
```

```{r housekeeping, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# Housekeeping
#rm(list=ls())
#getwd()
```


# Residency index

This doc contains Ri analyses for sharks, following email discussion 7 Aug 2022:

- Sharks #1: Ri for each species for each reef - covered in this doc/script
- Sharks #2: large-scale movement map (separate doc/script)  
- Sharks #3: blue-water movements within Holmes and Flinders movement (separate doc/script)  
  

The residency index is the number of days an animal was detected at each receiver (site or station residency) or reef (reef or installation residency) divided by the number of days monitored (i.e. number of days from the tagging date to the date of receiver retrieval) (Papastamatiou et al. 2010; Espinoza et al. 2011).



# Data load and wrangling

Data wrangling and station/installation Ri calculations conducted in separate scripts
```{r load-data, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
source("code/ri_installation.R")
```


# Relevel installation_name
```{r}
installation_ri %$% 
  summary(installation_name)

installation_ri <- installation_ri %>% 
  mutate(installation_name = fct_relevel(installation_name, c('Osprey', 'Bougainville', 'Holmes', 'Flinders'))) 
```



# Split up by reef {.tabset .tabset-faded}

## Osprey  
### NB Osprey has TP tagged animals so we need a way of handling this.
Also only want GTS
```{r osprey-ri, echo=FALSE, message=FALSE, warning=FALSE}
sharkri_osprey <- 
  installation_ri %>% 
  filter(installation_name == 'Osprey') %>% 
  filter(Scientific_name == "Carcharhinus amblyrhynchos") %>% 
  filter(tag_installation == "Osprey") %>% 
  #filter(Type != "pinger") %>% 
  group_by(Serial) %>% 
  slice_min(ri_installation) %>%   # Leaves in the highest value of the 2 Ri scores for each animal (one from T and one from P)
  ungroup() %>% 
  group_by(Serial, ri_installation) %>% # Then if there are animals that have the same Ri for both T and P, get rid of one of them
  slice(1) %>% 
  ungroup() %>% 
  arrange(Serial)

sharkri_osprey
```



## Bougainville
```{r osprey-ri, echo=FALSE, message=FALSE, warning=FALSE}
sharkri_bougainville <- 
  installation_ri %>% 
  filter(installation_name == 'Bougainville')
```

## Holmes
```{r osprey-ri, echo=FALSE, message=FALSE, warning=FALSE}
sharkri_holmes <- 
  installation_ri %>% 
  filter(installation_name == 'Holmes')
```

## Flinders
```{r osprey-ri, echo=FALSE, message=FALSE, warning=FALSE}
sharkri_flinders <- 
  installation_ri %>% 
  filter(installation_name == 'Flinders')
```












# Summary stats 
  
## Osprey {.tabset .tabset-faded}
```{r grs-stats-1, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
(osprey_stats <- 
  sharkri_osprey %>% 
  group_by(Scientific_name) %>% 
  summarise(mean = mean(ri_installation), sd = sd(ri_installation), se = std.error(ri_installation)) %>% 
  mutate_if(is.numeric, round, 2)) 

# Check again but exclude the two individuals that did not stay around for long
(osprey_stats <- 
  sharkri_osprey %>% 
  filter(transmitter_id != "A69-9001-64092") %>% 
  filter(transmitter_id != "A69-9001-64109") %>%   
  group_by(Scientific_name) %>% 
  summarise(mean = mean(ri_installation), sd = sd(ri_installation), se = std.error(ri_installation)) %>% 
  mutate_if(is.numeric, round, 2))


#osprey_stats %>%   write.csv("../output/sharkri_osprey.csv")
```


```{r grs-stats-1, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
ri_osprey_bar <- 
  osprey_stats %>% 
  ggplot(aes(x = Scientific_name, y = mean)) +
  geom_bar(stat="identity", position="dodge", color="black",fill = "steelblue", width = 0.95) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9)) +
  #cale_x_discrete(labels = c("Silvers", "Greys"))+
  scale_x_discrete(labels = NULL)+
  scale_y_continuous(expand = c(0,0), limits = c(0,1), breaks = c( 0.4, 0.8), position = "right") +
  theme(#panel.grid = element_line(colour = "#ECEFF1"),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        #axis.line = element_line(),
        panel.background = element_rect(fill = "white", colour = "black"),
        plot.background = element_rect(fill = "transparent", colour = "transparent"),
        legend.position = "bottom")  +
  annotate("text", x = 1, y = 0.9, label = "Osprey", size = 3, fontface = 2) +
  labs(y= "", x = "")

ri_osprey_bar
  
#ggsave(ri_osprey_bar, filename = "../output/ri_osprey_bar.png", width = 160, height = 100, units = 'mm', dpi = 600)
```






## Bougainville {.tabset .tabset-faded}
```{r boug-stats, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
bougainville_stats <- 
  sharkri_bougainville %>% 
  filter(Org_type == "Elasmobranch") %>% 
  group_by(Scientific_name) %>% 
  summarise(mean = mean(ri_installation), sd = sd(ri_installation), se = std.error(ri_installation)) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  print() 

#bougainville_stats %>%   write.csv("../output/sharkri_bougainville.csv")

ri_bougainville_bar <- 
  bougainville_stats %>% 
  ggplot(aes(x = Scientific_name, y = mean)) +
  geom_bar(stat="identity", position="dodge", color="black",fill = "springgreen", width = 0.95) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9)) +
  #scale_x_discrete(labels = c("Silvers", "Greys"))+
  scale_x_discrete(labels = NULL)+
  scale_y_continuous(expand = c(0,0), limits = c(0,1), breaks = c( 0.4, 0.8), position = "right") +
  theme(#panel.grid = element_line(colour = "#ECEFF1"),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        #axis.line = element_line(),
        panel.background = element_rect(fill = "white", colour = "black"),
        plot.background = element_rect(fill = "transparent", colour = "transparent"),
        legend.position = "bottom")  +
  #annotate("text", x = 1, y = 0.9, label = "Bougainville", size = 3, fontface = 2) +
  annotate("text", x = 1.2, y = 0.9, label = "Bougainville", size = 3, fontface = 2) +
  labs(y= "", x = "")

ri_bougainville_bar

#ggsave(ri_bougainville_bar, filename = "../output/ri_bougainville_bar.png", width = 160, height = 100, units = 'mm', dpi = 600)
```




## Holmes {.tabset .tabset-faded}
```{r grs-stats-1, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
holmes_stats <- 
  sharkri_holmes %>% 
  filter(Org_type == "Elasmobranch") %>% 
  group_by(Scientific_name) %>% 
  summarise(mean = mean(ri_installation), sd = sd(ri_installation), se = std.error(ri_installation)) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  print() 

#holmes_stats %>%   write.csv("../output/sharkri_holmes.csv")

ri_holmes_bar <- 
  holmes_stats %>% 
  ggplot(aes(x = Scientific_name, y = mean)) +
  geom_bar(stat="identity", position="dodge", color="black",fill = "yellow", width = 0.95) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9)) +
  #scale_x_discrete(labels = c("Silvers", "Greys"))+
  scale_x_discrete(labels = NULL)+
  scale_y_continuous(expand = c(0,0), limits = c(0,1), breaks = c( 0.4, 0.8)) +
  theme(#panel.grid = element_line(colour = "#ECEFF1"),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        #axis.line = element_line(),
        panel.background = element_rect(fill = "white", colour = "black"),
        plot.background = element_rect(fill = "transparent", colour = "transparent"),
        legend.position = "bottom")  +
  annotate("text", x = 1, y = 0.9, label = "Holmes", size = 3, fontface = 2) +
  labs(y= "", x = "")

ri_holmes_bar

#ggsave(ri_holmes_bar, filename = "../output/ri_holmes_bar.png", width = 160, height = 100, units = 'mm', dpi = 600)
```

## Flinders {.tabset .tabset-faded}
```{r grs-stats-1, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
flinders_stats <- 
  sharkri_flinders %>% 
  filter(Org_type == "Elasmobranch") %>% 
  group_by(Scientific_name) %>% 
  summarise(mean = mean(ri_installation), sd = sd(ri_installation), se = std.error(ri_installation)) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  print() 

#flinders_stats %>%   write.csv("../output/sharkri_flinders.csv")

ri_flinders_bar <- 
  flinders_stats %>% 
  ggplot(aes(x = Scientific_name, y = mean)) +
  geom_bar(stat="identity", position="dodge", color="black",fill = "coral", width = 0.95) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9)) +
  scale_x_discrete(labels = c("Silvertip", "Grey Reef"))+
  scale_y_continuous(expand = c(0,0), limits = c(0,1), breaks = c( 0.4, 0.8)) +
  theme(#panel.grid = element_line(colour = "#ECEFF1"),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        #axis.line = element_line(),
        axis.text.x = element_text(size = 7),
        panel.background = element_rect(fill = "white", colour = "black"),
        plot.background = element_rect(fill = "transparent", colour = "transparent"),
        legend.position = "bottom")  +
  annotate("text", x = 1, y = 0.9, label = "Flinders", size = 3, fontface = 2) +
  labs(y= "", x = "")

ri_flinders_bar

#ggsave(ri_flinders_bar, filename = "../output/ri_flinders_bar.png", width = 160, height = 100, units = 'mm', dpi = 600)
```


## Plot all together

```{r combined, fig.width=10, fig.height=12}

ri_combined_bar <- 
ri_osprey_bar/ri_bougainville_bar/ri_holmes_bar/ri_flinders_bar


ri_combined_bar


ggsave(ri_combined_bar, filename = "../output/ri_combined_bar.png", width = 100, height = 160, units = 'mm', dpi = 300)


```





# Sex

## Greys
```{r grs-stats-2, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
grs_sex_stats <- 
  ri_greys %>% 
  group_by(Sex) %>% 
  summarise(mean = mean(ri_installation), sd = sd(ri_installation), se = std.error(ri_installation)) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  print()

grs_sex_stats %>% 
  write.csv("../output/ri_greys_sex.csv")

grs_ri_sex_bar <-
  grs_sex_stats %>% 
  ggplot(aes(x = Sex, y = mean)) +
  geom_bar(stat="identity", position="dodge", color="black", width = 0.95) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9)) +
  scale_y_continuous(expand = c(0,0), limits = c(-0.02,1), breaks = c(0, 0.2, 0.4, 0.6, 0.8)) +
  scale_x_discrete(labels = c('Female', 'Male')) +
  theme(axis.text.y = element_blank(), # Can get rid of this as plotting next to the installation plot
        axis.title.y = element_blank(), # Ditto
        axis.ticks.y = element_blank(), # Ditto
        panel.grid = element_line(colour = "#ECEFF1"),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        panel.background = element_rect(fill = "blue"),
        plot.background = element_rect(fill = "transparent", colour = "transparent"),
        legend.position = "bottom")  +
  labs(y= "Ri (mean ± SE)", x = "Sex")

grs_ri_sex_bar

#ggsave(grs_ri_sex_bar, filename = "../output/ri_greys_sex_bar.png", width = 80, height = 100, units = 'mm', dpi = 600)

```


## Silvers
```{r silvers-stats-2, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
silvers_sex_stats <- 
  ri_silvers %>% 
  group_by(Sex) %>% 
  summarise(mean = mean(ri_installation), sd = sd(ri_installation), se = std.error(ri_installation)) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  print()

silvers_ri_sex_bar <-
  silvers_sex_stats %>% 
  ggplot(aes(x = Sex, y = mean)) +
  geom_bar(stat="identity", position="dodge", color="black", width = 0.95) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9)) +
  scale_y_continuous(expand = c(0,0), limits = c(-0.02,1), breaks = c(0, 0.2, 0.4, 0.6, 0.8)) +
  scale_x_discrete(labels = c('Female', 'Male')) +
  theme(axis.text.y = element_blank(), # Can get rid of this as plotting next to the installation plot
        axis.title.y = element_blank(), # Ditto
        axis.ticks.y = element_blank(), # Ditto
        panel.grid = element_line(colour = "#ECEFF1"),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent", colour = "transparent"),
        legend.position = "bottom")  +
  labs(y= "Ri (mean ± SE)", x = "Sex")

ggsave(silvers_ri_sex_bar, filename = "../output/ri_silvers_sex_bar.png", width = 80, height = 100, units = 'mm', dpi = 600)
silvers_ri_sex_bar

```


### Plot together
```{r grs-ri-plots, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
sex_riplot <- 
silvers_ri_sex_bar + grs_ri_sex_bar +
  plot_layout(widths = c(2,1))
ggsave(greys_riplot, filename = "../output/riplot_greys.png", width = 160, height = 100, units = 'mm', dpi = 600)
```

