---
title: "Analysing residency indices - Teleosts"
author: "Ben Cresswell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
knit: (function(inputFile, encoding) { 
      out_dir <- "../output";
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), out_dir, 'Ri_teleost_analysis.html')) })
output: 
 html_document:
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 4
    fig_width: 4
    highlight: textmate
    theme: spacelab
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: inline
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r packages, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# Packages
library(knitr)
library(kableExtra)
library(sp)
library(rgdal)
library(rgeos)
library(adehabitatHR)
library(leaflet)
library(ggmap)    # for fortifying shapefiles
library(readxl)
library(scatterpie)
library(plotrix)   # Calculates SE
library(collapse)
library(magrittr)
library(tidyverse)
```


```{r housekeeping, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# Housekeeping
#rm(list=ls())
#getwd()
```


# Residency index

This document contains Ri analyses for teleosts, following email discussion 7 Aug 2022:

- Teleosts #1 - Ri for tagging station (on Osprey), and..  
- Teleosts #4 - Ri for alternative stations visited (again Osprey only)  
The other 2 teleost analyses (distance and timing of movement) are handled in another markdown doc.  

The residency index is the number of days an animal was detected at each receiver (site or station residency) or reef (reef or installation residency) divided by the number of days monitored (i.e. number of days from the tagging date to the date of receiver retrieval) (Papastamatiou et al. 2010; Espinoza et al. 2011).  

Teleost dataset is based on 11 GTs (10 with sensor tags and 1 with pinger only), 5 black trevally and 1 coral trout.  

# Data load and wrangling

Data wrangling and station/installation Ri calculations conducted in separate scripts
```{r load-data, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
source("ri_installation.R")
source("ri_station.R")
```


# Installation Ri Analysis

## Comparing installation Ri between teleost taxa
```{r teleost-inst-ri-plot, echo=FALSE, message=FALSE, warning=FALSE}
teleost_installation_ri <-   
installation_ri %>% 
  filter(Org_type == 'Teleost') %>% 
  group_by(Scientific_name) %>% 
  summarise(mean = mean(ri_installation), sd = sd(ri_installation), se = std.error(ri_installation)) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  print

teleost_installation_ri %>% 
  write.csv("../output/ri_installation_teleosts.csv")

teleost_installation_ri_plot <- 
teleost_installation_ri %>% 
  ggplot(aes(x = Scientific_name, y = mean)) +
  geom_bar(stat="identity", position="dodge", color="black", width = 0.95) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9))+
  scale_y_continuous(expand = c(0,0), limits = c(-0.02,.7), breaks = c(0, 0.2, 0.4, 0.6, 0.8)) +
  theme(panel.grid = element_line(colour = "#ECEFF1"),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent", colour = "transparent")) +
  #ggtitle("Installation Ri (Osprey) for teleost taxa") +
  labs(y= "Ri (mean ± SE)", x = "Taxa")
ggsave(teleost_installation_ri_plot, filename = "../output/inst_ri_teleost_bar.png", width = 160, height = 100, units = 'mm', dpi = 600)

```
  
#### Notes    
- Only one individual trout in data set so no sd or se.   


# Station Ri analysis 

## Extract Ri values for each taxa {.tabset .tabset-faded}

### Caranx ignobilis
```{r gt-ri, echo=FALSE, message=FALSE, warning=FALSE}
station_ri_gts <- 
  station_ri %>% 
  filter(Scientific_name == 'Caranx ignobilis')
  
station_ri_gts %>% 
  kbl() %>%
  kable_minimal()
```

### Caranx lugubris
```{r cl-ri, echo=FALSE, message=FALSE, warning=FALSE}
station_ri_lugub <- 
  station_ri %>% 
  filter(Scientific_name == 'Caranx lugubris') 

station_ri_lugub %>% 
  kbl() %>%
  kable_minimal()
```

### Plectropomus laevis
```{r pl-ri, echo=FALSE, message=FALSE, warning=FALSE}
station_ri_trout <- 
  station_ri %>% 
  filter(grepl('laev', Scientific_name)) 

station_ri_trout %>% 
  kbl() %>%
  kable_minimal()
```


## Station Ri sumary stats and barplots

### Giant trevally (Caranx ignobilis)
```{r gt-bar, echo=FALSE, message=FALSE, warning=FALSE}
station_ri_stats_gts <- 
  station_ri_gts %>% 
  group_by(station_name, station_name_long) %>% 
  summarise(mean = mean(ri_station), sd = sd(ri_station), se = std.error(ri_station)) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  print

station_ri_stats_gts %>% 
  write.csv("../output/ri_station_gts.csv")

ri_gts_bar <- 
station_ri_stats_gts %>% 
  ggplot(aes(x = station_name, y = mean)) +
  geom_bar(stat="identity", position="dodge", color="black", width = 0.95) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9))+
  scale_y_continuous(expand = c(0,0), limits = c(-0.02,0.4), breaks = c(0, 0.2, 0.4, 0.6, 0.8)) +
  theme(panel.grid = element_line(colour = "#ECEFF1"),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent", colour = "transparent"),
        legend.position = "bottom") +
  labs(y= "Ri (mean ± SE)", x = "Osprey station code")

ri_gts_bar

ggsave(ri_gts_bar, filename = "../output/ri_gts_bar.png", width = 160, height = 100, units = 'mm', dpi = 600)
```
  
#### Notes    
- Duplicates (T/P) already filtered out in wrangling script  
- Detections centered on CS-03 and CS-04 -> right in lagoon entrance and the edge of the lagoon.


### Black trevally (Caranx lugubris)
```{r lug-bar, echo=FALSE, message=FALSE, warning=FALSE}
station_ri_stats_lugub <- 
station_ri_lugub %>% 
  group_by(station_name, station_name_long) %>% 
  summarise(mean = mean(ri_station), sd = sd(ri_station), se = std.error(ri_station)) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  print

station_ri_stats_lugub %>% 
  write.csv("../output/ri_station_lugub.csv")

ri_lugub_bar <- 
station_ri_stats_lugub %>% 
  ggplot(aes(x = station_name, y = mean)) +
  geom_bar(stat="identity", position="dodge", color="black", width = 0.95) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9))+
  scale_y_continuous(expand = c(0,0), limits = c(-0.02,0.6), breaks = c(0, 0.2, 0.4, 0.6, 0.8)) +
  theme(panel.grid = element_line(colour = "#ECEFF1"),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent", colour = "transparent"),
        legend.position = "bottom") +
  labs(y= "Ri (mean ± SE)", x = "Osprey station code")

ri_lugub_bar

ggsave(ri_lugub_bar, filename = "../output/ri_lugub_bar.png", width = 160, height = 100, units = 'mm', dpi = 600)
```
  
#### Notes  
- Note the absence of any detections from CS-04 or CS-05 (i.e. the Lagoon stations)

### Coral trout (Plectropomus laevis)
```{r trout-bar, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
station_ri_stats_trout <- 
station_ri_trout %>% 
  group_by(station_name, station_name_long) %>% 
  summarise(mean = mean(ri_station), sd = sd(ri_station), se = std.error(ri_station)) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  print

station_ri_stats_trout %>% 
  write.csv("../output/ri_station_trout.csv")

ri_trout_bar <- 
station_ri_stats_trout %>% 
  ggplot(aes(x = station_name, y = mean)) +
  geom_bar(stat="identity", position="dodge", color="black", width = 0.95) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9))+
  scale_y_continuous(expand = c(0,0), limits = c(-0.02,0.1), breaks = c(0, 0.2, 0.4, 0.6, 0.8)) +
  theme(panel.grid = element_line(colour = "#ECEFF1"),
        panel.border = element_rect(colour = "black", fill = "transparent"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent", colour = "transparent"),
        legend.position = "bottom") +
  labs(y= "Ri (mean ± SE)", x = "Osprey station code")

ri_trout_bar

ggsave(ri_trout_bar, filename = "../output/ri_trout_bar.png", width = 160, height = 100, units = 'mm', dpi = 600)

```
  
#### Notes  
- Only 1 individual with 16 observations so a bit meaningless to present separately




