---
title: "tidy EDA - Sensor Data"
aauthor: "Ben Cresswell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
 html_document:
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 4
    fig_width: 4
    highlight: textmate
    theme: spacelab
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: inline
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Note: Need to run the tidyeda.Rmd first to subset the required objects

# Load required packages
```{r packages, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(sp)
library(rgdal)
library(rgeos)
#library(adehabitatHR) # This package makes select clash with dplyr
library(leaflet)
library(tidyverse)
```

# First, let's load the full list of tags deployed in the region
```{r warning=FALSE}
#rm(list=ls()) # Clear out environment if necessary
source("regional_tag_list.R", local = knitr::knit_global())
rm("regional_shark_list", "regional_teleost_list") # Remove the individual shark and telost lists as we don't need them separately (for now)
```


# Next we are going to need a list of all our sensor tags deployed
This is stored in 2 separate files which can be read in and then combined
```{r load-tagged-animals2}
project_tag_list <- read_excel("../data/csmp_sharks.xlsx", trim_ws = TRUE) %>% 
  dplyr::select(!c(6,7,8)) %>% 
  rbind(read_excel("../data/csmp_teleosts.xlsx", trim_ws = TRUE) %>% 
  dplyr::select(c(1,2,3,4,5,9,10))) %>% 
  mutate_if(is.character, as.factor) %>% # Sorts out variables
  dplyr::select('ID') %>% # Don't want duplicated columns
  merge(regional_tag_list, by = 'ID', no.dups=TRUE)
```


## And then filter out just the sensor tags
```{r load-tagged-animals2}
sensor_tag_list <- project_tag_list %>% 
  filter(Type != 'pinger')
```
We have 25 tagged animals out there so there should be 50 in this list (and there are 50!)

# Now we have a list of tags we can use this to extract all the sensor observations from our detection data

# Load detection data
```{r}
# Going to use the ATT set up data as it has the most appropriately/usefully labelled columns/variables
load(file = "../data/RData/attsetupdata.RData")

str(setupdata)
# Get rid of unnecessary columns...

setupdata <- setupdata %>% 
  select(!c(7,8,9,10,15,16,19,20,21,22,23,24))

```




######## NOTES

Just need to make sure that the setupdata and sensor data has imported ok to this point!!




























## Need to filter out sensor only data
```{r}
sensordata <- sensor_tag_list %>% 
  dplyr::select('transmitter_id') %>%  # Don't want duplicate columns/variables
  merge(setupdata)
```

So now we have a detection file just for sensor data. 
Need to calibrate all the pressure and temp readings - this will require the sensor_type, sensor_value, sensor_units, slope and intercept


```{r}
sensordata <- sensordata %>% 
  mutate(calibrated_sensor_value = sensor_value*sensor_slope+sensor_intercept) %>% 
  mutate(sensor_unit = case_when(grepl('press', sensor_type) ~ "Meters(Depth)",
                                   grepl('temp', sensor_type) ~ "°C(Temp)")) # %>% 
#  dplyr::select(scientific_name, transmitter_id, sensor_value, sensor_slope, sensor_intercept, sensor_type, calibrated_sensor_value, sensor_unit) # Just makes a smaller file to check that everything working

```

# Some 

```{r}
shark_sensors <- sensordata %>%
  filter(str_detect(scientific_name, str_c(c("Carcharhinus"))))

```



```{r}
CS123_Temp <- sensordata %>%
  filter(str_detect(transmitter_id, str_c(c("6251"))))

CS123_Temp
```














Need to pull out sharks and teleosts separately and combine

```{r}
## TELEOSTS ##

# Filter out just our teleost sensor data
teleost_sensor_data <- sensor_data %>% 
  filter(str_detect(`Transmitter`, "9007-62")) # All our V13 sensor tags start with this #

# Check how many individual tags present
teleost_sensors <- teleost_sensor_data %>% 
  distinct(Transmitter) 

# 14 sensors - 7 fish. One missing: 6259/6260/CS142 Caranx ignobilis tagged on 30/10/2021 :(


## SHARKS ##

# Filter out just shark sensor data
shark_sensor_data <- sensor_data %>% 
  filter(str_detect(`Transmitter`, "9004-140")) # All our V16 sensor tags start with this #

shark_sensors <- shark_sensor_data %>% 
  distinct(Transmitter) 

# 30 sensors - 15 sharks. All present and correct :)
```


```{r}


# Check how many animals
sensordata %>% 
  distinct(transmitter_id) # 51

```


## Create dataframe with details of animals detected



## And use to pull out individual sensor tag observations

```{r}

```




























