---
title: "Present vs Absent"
author: "Ben Cresswell"
date: "31/03/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
getwd()
#rm(list=ls())
```


# This Rmd figures out which animals disappeared from the array and which are from outside our study

## This basically requires 3 sources of information/data which will be loaded and used in this analysis

1. A list of tags that have been deployed across the wider region
2. A list of tags that have been actively deployed as part of the CSMP project
3. A list of all tags that have turned up in our array during the period of interest (obtained from either alldata or setupdata would work I think)

## From this info we can extract:
4. A list of tags that we don't recognise (unknowns - these can be checked against IMOS and Vemco)
5. A list of tags that haven't turned up at all during the deployment


# Packages
```{r}
library(writexl)
library(readxl)
library(lubridate)
library(tidyverse)
```


# Read in data

## 1. List of tags across wider region
Sourced from another R script regional_tag_list.R
```{r load-reg-tags, message=FALSE, warning=FALSE}
#rm(list=ls())
source("../code/regional_tag_list.R")
#rm("regional_shark_list", "regional_teleost_list") # Remove the individual shark and telost lists as we don't need them separately (for now)
```

## 2. List of just the CSMP 2021-22 tagged animals
Sourced from another R script project_tag_list.R
```{r load-proj-tags, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
source("../code/project_tag_list.R")
```


## 
```{r load-tagged-animals2}
project_tag_list <- project_serials %>% 
  merge(regional_tag_list, by = 'ID') # Adds in other variables we might need
```









## OR
```{r load-tagged-animals2}
project_tag_list <- read_excel("../data/csmp_sharks.xlsx", trim_ws = TRUE)# %>% 
  dplyr::select(!c(6,7,8)) %>% 
  rbind(read_excel("../data/csmp_teleosts.xlsx", trim_ws = TRUE) %>% 
  dplyr::select(c(1,2,3,4,5,9,10)))# %>% 
  mutate_if(is.character, as.factor) %>%  # Sorts out variables
  merge(regional_tag_list, by = 'ID') # Adds in other variables we might need
```


## Check
```{r}
#summary(csmp_animals$Scientific_name)
#summary(csmp_animals$Species)
#summary(csmp_animals$Location)
```


## 3. List of detected tags

First load detection data
```{r}
load(file = "../data/RData/alldata.RData")
# OR
#load(file = "../data/RData/attsetupdata.RData")
```

# Then filter out detected tag information from the regional tag list
```{r}
detected_tag_list <- alldata %>% 
  distinct(transmitter_id) %>% 
  merge(regional_tag_list, all.x = TRUE) # Need to keep all the unkowns in so all.x = TRUE. Heaps of NAs in this df because of this
```

So, just looking at the number of observations in these 3 dataframes we can figure out how many tags involved wth each (note some of these will be duplicated animal due to dual sensor IDs)

1. Regional tags: 596 tag IDs
2. Project tags:  137 tag IDs
3. Detected tags: 196 tag IDs


# Now we have our first 3 lists of tags, we can figure out the remaining two - unknown tags and missing tags


## 4. Unknown tags

```{r}
unknown_tag_list <- anti_join(detected_tag_list, regional_tag_list, by = 'transmitter_id') %>% # This function produces a list of unique 
  print()
```

So 68 transmitter IDs have been detected that are not from any of our records
## Check out separate R script (unknown_tag_asst.Rmd) to export a list that can be used to check these IDs in the IMOS Mystery Tag Tool and Transmitter databases


## 5. Missing tags

We know we have 196 detected transmitter IDs in our detection database, but how many of these are ones we tagged for the CSMP project?

## Therefore firstly need to generate a list of project detections

```{r}
project_detection_list <- project_tag_list %>% 
  merge(detected_tag_list, by = 'transmitter_id')
```
Only 125 of the 137 deployed transmitter IDs - there's 12 missing. Let's figure out which ones they are

## Which ones not detected
```{r}
missing_tag_list <- project_tag_list %>% 
  anti_join(project_detection_list, by = 'transmitter_id') #%>% 
```
This list contains 12 transmitter_ids, however this doesn't equate to separate animals as some of them are dual sensor (T/P) tags

# Actually animals missing
```{r}
missing_animal_list <- missing_tag_list %>% 
  group_by(Date.x, Scientific_name.x, Location.x, Site.x, Model) %>% 
  distinct(Serial)

print(missing_animal_list)
```

3 GTs with T/Ps missing from this list - one tagged in October (genuinely missing) and 2 tagged in March 2022 (haven't had a chance to be detected yet)
6 sharks missing (5 silvers and 1 grey)


```{r}
non_csmp_sharks <- csmp_sharks[20] %>% 
  anti_join(regional_shark_list)
```






