---
title: "Present vs Absent"
author: "Ben Cresswell"
date: "31/03/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
getwd()
#rm(list=ls())
```


# This Rmd figures out which animals disappeared from the array and which are from outside our study

## This basically requires 3 sources of information/data which will be loaded and used in this analysis

1. A list of tags that have been deployed across the wider region
2. A list of tags that have been actively deployed as part of the CSMP project
3. A list of all tags that have turned up in our array during the period of interest (obtained from either alldata or setupdata would work I think)

## From this info we can extract:
4. A list of tags that we don't recognise (unknowns - these can be checked against IMOS and Vemco)
5. A list of tags that haven't turned up at all during the deployment


# Packages
```{r}
library(writexl)
library(readxl)
library(lubridate)
library(tidyverse)
```


# Read in data

## 1. List of tags from across wider region
Sourced from another R script regional_tag_list.R
```{r load-reg-tags, message=FALSE, warning=FALSE}
#rm(list=ls())
source("../code/regional_tag_list.R")
#rm("regional_shark_list", "regional_teleost_list") # Remove the individual shark and telost lists as we don't need them separately (for now)
```

## 2. List of just the CSMP 2021-22 tagged animals
Sourced from another R script project_tag_list.R
```{r load-proj-tags, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
source("../code/project_tag_list.R")
```

## 3. List of detected tags
First load detection data
```{r}
load(file = "../data/RData/alldata.RData")
# OR
#load(file = "../data/RData/attsetupdata.RData")
```

# Then filter out detected tag information from the regional tag list
```{r}
detected_tag_list <- alldata %>% 
  distinct(transmitter_id) %>% 
  merge(regional_tag_list, all.x = TRUE) # Need to keep all the unknowns in so all.x = TRUE. Heaps of NAs in this df because of this
```

So, just looking at the number of observations in these 3 dataframes we can figure out how many tags involved wth each (note some of these will be duplicated animal due to dual sensor IDs)

1. Regional tags: 596 tag IDs
2. Project tags:  137 tag IDs
3. Detected tags: 196 tag IDs

We have more detected tags than project tags. Some of these are likely from the regional tag group and some will be ghost detections. There may also be animals that we tagged that immediately disappeared from the array. We can check all of this using these first 3 lists of tags, producing two further lists - unknown tags and missing tags.


## 4. Unknown tags
These will be ones that we don't have information for, even in the regional tag list:
```{r}
unknown_tag_list <- anti_join(detected_tag_list, regional_tag_list, by = 'transmitter_id') %>% # This function produces a list of unique 
  print()
```

So 68 transmitter IDs have been detected that are not from any of our records
## This is handled in a separate R script (unknown_tag_asst.Rmd) which exports a list that can be used to check these IDs in the IMOS Mystery Tag Tool and Transmitter databases


## 5. Missing tags

We know we have 196 detected transmitter IDs in our detection database, but how many of these are ones we tagged for the CSMP project?

## Therefore firstly need to generate a list of project detections

```{r}
project_detection_list <- project_tag_list %>% 
  merge(detected_tag_list, by = 'transmitter_id')
```
Only 125 of the 137 deployed transmitter IDs - there's 12 missing. Let's figure out which ones they are

## Which ones not detected
```{r}
missing_tag_list <- project_tag_list %>% 
  anti_join(project_detection_list, by = 'transmitter_id') %>% 
  print
```
This list contains 12 transmitter_ids, however this doesn't equate to separate animals as some of them are dual sensor (T/P) tags

# Actual animals missing
```{r}
missing_animal_list <- missing_tag_list %>% 
  group_by(Date, Scientific_name, Location, Site, Model) %>% 
  distinct(Serial)

print(missing_animal_list)
```

3 GTs with T/Ps missing from this list - one tagged in October (genuinely missing) and 2 tagged in March 2022 (haven't had a chance to be detected yet)
6 sharks missing (5 silvers and 1 grey)


# Actual animals should there have been?
```{r}
project_animal_list <- project_tag_list %>% 
  group_by(Date, Scientific_name, Location, Site, Model) %>% 
  distinct(Serial)

print(project_animal_list)
```











```{r}
non_csmp_sharks <- csmp_sharks[20] %>% 
  anti_join(regional_shark_list)
```

# A check to see how many GRS tagged on Osprey
```{r}
project_tag_list %>% 
  filter(Location == 'Osprey',
         Org_type == 'Elasmobranch')
```




