---
title: "Analysing Teleost Movement Timing and Distance"
author: "Ben Cresswell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
knit: (function(inputFile, encoding) { 
      out_dir <- "../output";
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), out_dir, 'teleost_movement_timingdistance.html')) })
output: 
 html_document:
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 6
    fig_width: 14
    highlight: textmate
    theme: spacelab
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: inline
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')
```


```{r packages, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# Packages
library(sp)
library(rgdal)
library(rgeos)
#library(tibbletime) # Time series management - don't think we need. lubridate prob better.
library(adehabitatHR)
library(leaflet)
library(ggmap)    # for fortifying shapefiles
library(readxl)
library(scatterpie)
library(plotrix)   # Calculates SE
library(collapse)
library(magrittr)
library(tidyverse)
```


```{r housekeeping, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# Housekeeping
#rm(list=ls())
#getwd()
```


# Data load and wrangling {.tabset .tabset-faded}

## Load data
### Going to load the main dataset and tease out movement time from there
```{r load-data, message=FALSE, warning=FALSE}
load(file = "../data/RData/alldata.RData")
```

## Filter out
### Only want teleosts for now
```{r teleost-filter}
teleosts <- 
  alldata %>% 
  filter(Org_type == 'Teleost')
```


## Checks
### Check how many we have
```{r df-check, echo=FALSE, message=FALSE, warning=FALSE}
teleosts %>% 
  dplyr::select(transmitter_id) %>% 
  distinct() 
```
  
- 10 We know we are missing 3 of the sensor tagged individuals and that we have 13 project serials out there. 13-3 = 10. Perfect.

## Project tag list
### Check against project tag list
```{r check-proj-teleosts, echo=FALSE, message=FALSE, warning=FALSE}
# Can check against project_teleosts df
source('project_tag_list.R')
project_serials_teleosts %>% 
  group_by(Serial) %>% 
  distinct()
```

  
####  

# Exploring timing of movements

## Abacus plots
```{r teleost-abacus, echo=FALSE, message=FALSE, warning=FALSE}
teleosts %>% 
  ggplot(aes(x = detection_timestamp, y = station_name)) + 
  xlab("Date") + 
  ylab("Station") +
  geom_point() +
  facet_wrap(~ transmitter_id)
```
  
- Hard to discern any temporal pattern from this abacus plot



# Day vs night {.tabset .tabset-faded}

```{r teleosts-mutate-daynight, echo=FALSE, message=FALSE, warning=FALSE}
teleosts <- 
  teleosts %>%
  mutate(hour = hour(detection_timestamp),
         minute = minute(detection_timestamp),
         time = hm(paste(hour, minute))) %>% 
  mutate(tod = case_when(hour %in% (6:18) ~ "Day",
         TRUE ~ "Night"))
```


## Bar plots
```{r tab-plot, echo=FALSE, message=FALSE, warning=FALSE}
# Day
teleosts %>% 
  filter(tod == 'Day') %>% 
  dplyr::select(station_name, station_name_long) %>% 
  group_by(station_name, station_name_long) %>% 
  mutate(stationobs = n()) %>% 
  distinct %>% 
  arrange(station_name) %>% 
  #print() %>% 
  ggplot(aes(x = station_name, y = stationobs)) +
  geom_bar(stat="identity", position="dodge", color="black") +
  #geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9)) +
  ggtitle("Day") +
  labs(y= "No observations", x = "Osprey station code")

# Night
teleosts %>% 
  filter(tod == 'Night') %>% 
  dplyr::select(station_name, station_name_long) %>% 
  group_by(station_name, station_name_long) %>% 
  mutate(stationobs = n()) %>% 
  distinct %>% 
  arrange(station_name) %>% 
  #print() %>% 
  ggplot(aes(x = station_name, y = stationobs)) +
  geom_bar(stat="identity", position="dodge", color="black") +
  #geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9)) +
  ggtitle("Night") +
  labs(y= "No observations", x = "Osprey station code")
```
  

## Tables
```{r}
# Day
teleosts %>% 
  filter(tod == 'Day') %>% 
  dplyr::select(station_name, station_name_long) %>% 
  group_by(station_name, station_name_long) %>% 
  mutate(stationobs = n()) %>% 
  distinct %>% 
  arrange(station_name) %>% 
  print() 


# Night
teleosts %>% 
  filter(tod == 'Night') %>% 
  dplyr::select(station_name, station_name_long) %>% 
  group_by(station_name, station_name_long) %>% 
  mutate(stationobs = n()) %>% 
  distinct %>% 
  arrange(station_name) %>% 
  print()

```
  
  
- Clearly higher number of detections during the day on CS-03 (Overnight Moorning) and CS-06 (Around the Bend), shifting to more detections at CS-04 (Lagoon 1) during the night. 
- Seems like a diurnal pattern of movement, likely for foraging/predation?
- Don't think we'll have enough data points to explore lunar patterns or longer cycles but might be worth a go.
filter(Scientific_name == 'Caranx ignobilis') %>%

# Important:
Not appropriate to present total numbers of detections due to autocorrelation issues, so will need to redo this analysis but using Ri as the base metric
However, will dig a bit deeper into the raw data for the coral trout (see separate script)

