---
title: "Transmitter data import and wrangling"
author: "Ben Cresswell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
 html_document:
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 4
    fig_width: 4
    highlight: textmate
    theme: spacelab
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: inline
---

This Rmd takes the Vue database (exported to csv format) and conducts EDA primarily using dplyr/tidyverse
Code initially taken from tutorial at: https://vinayudyawer.github.io/Animals-in-Motion-2018/Documents/OCS2018.html#session_4:_centres_of_activity_and_home_range_estimation

# PRELIMINARIES #

# Set up Rmd
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#rm(list=ls())
```

# Load required packages
```{r packages, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(writexl)
library(readxl)
library(lubridate)
library(tidyverse)
#library(VTrack) # Current R doesn't like VTrack - may need to install an earlier version..
```


# Load data
```{r}
#rm(list=ls())
load(file = "../data/RData/alldata.RData")
 # mutate(date=as.Date(detection_timestamp)) 
#Could also load the setup data file. Very similar but should be more in IMOS format
load(file = "../data/RData/attsetupdata.RData")

#alldata <- alldata %>% 
#  mutate(date=date(detection_timestamp))# adding a column with date of each detection (need later on)
setupdata <- setupdata %>% 
  mutate(date=date(detection_timestamp))# adding a column with date of each detection
```



```{r}
#head(alldata)
#glimpse(setupdata)
```

# Dataframe is massive - would be good to drill down into it

## First check names are all recorded correctly
```{r}
#head(alldata)
summary(alldata$Scientific_name)
summary(alldata$Common_name) # Multiple spellings for GTs but we can filter by sci name for those
```
## Questions
- Put laevis in or leave out? - work up map on that. Try to compare that with lunar cycles
- Also lunar cycles (or other) for GTs?


# Filter out by taxa 

## Sharks
```{r}
# All greys
grs_all <- 
  alldata %>% 
  filter(Common_name == 'Grey Reef')
  
# All silvertips
silvers_all <- alldata %>% 
  filter(Scientific_name == 'Carcharhinus albimarginatus')

# All tigers
tigers_all <- alldata %>% 
  filter(Common_name == 'Tiger shark')

```

## Teleosts
```{r}
# All trevallies
trevs <- alldata %>% 
  filter(str_detect(Scientific_name, str_c(c('Caranx'), collapse="|"))) # Includes lugubris

# All GTs
gts <- alldata %>% 
  filter(Scientific_name == 'Caranx ignobilis')

# The one P. laevis
trout <- alldata %>% 
  filter(Scientific_name == 'Plectopomus laevis') # Note the spelling mistake - will have to sort out later on
```



```{r}
# Greys at Osprey Reef
os_grs <- alldata %>% 
  filter(Location == 'Osprey') %>% 
  filter(Common_name == 'Grey Reef')

# Silvers at Osprey Reef
os_silvers <- alldata %>% 
  filter(Location == 'Osprey') %>% 
  filter(Scientific_name == 'Carcharhinus albimarginatus')

# Silvers at Holmes Reef
hr_silvers <- alldata %>% 
  filter(Location == 'Osprey') %>% 
  filter(Scientific_name == 'Carcharhinus albimarginatus')

summary(alldata$Location)

```




#

# Check how many animals
```{r}
os_grs %>% 
  distinct(transmitter_id) # 51
silvers %>% 
  distinct(transmitter_id) # 13
gts %>% 
  distinct(transmitter_id) # 11
trevs %>% 
  distinct(transmitter_id) # 16
trout %>%  
  distinct(transmitter_id) # 1
```



# Abacus plots
## GTs
```{r}
gts %>%
  ggplot(mapping = aes(x = detection_timestamp, y = as.factor(transmitter_id))) + 
  xlab("Date") + 
  ylab("Tag") +
  geom_point()

```


## Silvers
```{r}
silvers %>%
  ggplot(mapping = aes(x = detection_timestamp, y = as.factor(transmitter_id))) + 
  xlab("Date") + 
  ylab("Tag") +
  geom_point() 

```

## and faceted out by installation name (of where receiver was)
```{r fig.height = 10, fig.width = 16}
silv_ab <- silvers %>%
  ggplot(mapping = aes(x = detection_timestamp, y = installation_name)) + 
  xlab("Date") + 
  ylab("Tag") +
  geom_point() +
  facet_wrap(~ transmitter_id)
silv_ab
```
 64080 moved from Holmes to Flinders to Osprey over the year with a long gap of no detections
 
 

## Save to get a better look
```{r save-silver-ab}
#ggsave(filename = '../output/silver_abacus_overview.png', silv_ab, width = 1000, height = 600, units = 'mm', dpi = 300)
```























##### MY ORIGINAL GO...

# First will subset data to make manageable for experimentation
```{r}


#subsetdata <- alldata %>% 
 # filter(transmitter_id=="A69-9001-64090") # GRS from Osprey on trip 1

```

















## Now we have the master dataframe with all the necessary information in (VR2W location, animal info etc)
## Check how many tags tags recorded over the entire study

```{r}
detected_tags <- alldata %>% 
  distinct(transmitter_id) %>% 
  arrange(transmitter_id) %>% 
  glimpse()
```
- 196 total tag IDs detected during study so far
- We have ~112 physical tags deployed so it seems we are picking up a bunch of other animals/tags
- Some of these are sensor tags which have 2 Vue Tag IDs each so the number of detected tags should be more
- Some of the non-study tags may be ghosts or false readings. Need to investigate..


# Next steps:

1. Unknown tag assessment:
Need to check what Tag_IDs are appearing from outside both our study and Adams's master list (see the Rmd "unknown_tag_asst")
From these, determine which detections are bogus and which might be from real tagged animals (using the IMOS "Mystery Tag tool")

2. Known tags:
Need to split out tagged animals that are just from our specific CSMP study and those that are from the wider region, including tigers etc.

3. CSMP tags:
Same 

3. Sensor data:
Need to wrangle and calibrate sensor data

4. Abacus plots:
Going to try these first


















# Moving on...

# Split out 









# Sensor data wrangling

```{r}


# Filter out data from tags with temp and pressure sensors
sensor_data <- database_dep2_details2 %>% 
  filter(Sensor.Value!='NA')
```











### JUNK/ARCHIVE ###


# Box plots - numbers of detections per day
## Silvertips
```{r}
silvers %>%
  group_by(transmitter_id, date) %>% 
  summarise(DailyDetections= n()) %>% # use summarise to calculate numbers of detections per day per animal
  ggplot(mapping = aes(x = transmitter_id, y = DailyDetections)) + # define the aesthetic map (what to plot)
  xlab("Tag") + ylab("Number of detections per day") +
  geom_boxplot() # define the geometric object (how to plot it).. in this case a boxplot
```
## GTs
```{r}
trevs %>%
  group_by(transmitter_id, date) %>% 
  summarise(DailyDetections= n()) %>% # use summarise to calculate numbers of detections per day per animal
  ggplot(mapping = aes(x = transmitter_id, y = DailyDetections)) + # define the aesthetic map (what to plot)
  xlab("Tag") + ylab("Number of detections per day") +
  geom_boxplot() # define the geometric object (how to plot it).. in this case a boxplot
```












```{r}

```











