---
title: "Unknown tag assessment"
author: "Ben Cresswell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
 html_document:
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 4
    fig_width: 4
    highlight: textmate
    theme: spacelab
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: inline
---

This Rmd takes the combined database for the CSMP array and extracts detections of unknown tags/animals, for cross referencing against the IMOS database.

Last update: 16 June 2022 BJC (included Paul Butcher animals - these will need to be added to the big-movers work)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load required packages
```{r packages, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(writexl)
library(readxl)
library(lubridate)
library(tidyverse)
```


# Load database
```{r}
#rm(list=ls())
load(file = "../data/RData/alldata.RData")
```

# Create list of tags recorded over the entire study
```{r}
detected_tags <- alldata %>% 
  distinct(transmitter_id) %>% 
  arrange(transmitter_id) %>% 
  glimpse()
```
#196 total tag IDs
- We have ~112 transmitter_IDs deployed so it seems we are picking up a bunch of other animals/tags
- Some of these are sensor tags which have 2 Vue Tag IDs each so the number of detected tags should be more
- Some of the non-study tags may be ghosts or false readings. Need to investigate..



# Next step: make a list of tags we don't recognise

## First need to import list of all known tags deployed in the region

```{r}
source("regional_tag_list.R", local = knitr::knit_global())
```

```{r}
unknown_tags <- anti_join(detected_tags, regional_tag_list) %>% 
  separate(transmitter_id, c("Code", "Space", "ID")) %>% 
  mutate(ID = as.numeric(ID)) %>% 
  print()
```
So 68 'tags' have been recorded that are not from any of our project records
How does this look in the data? Are there lots of observations or might a lot of these be ghosts?

## Use the list of unknown tags to extract all of their observations from the main df:
```{r}
unknown_tag_observations <- unknown_tags %>% 
  merge(alldata)
```

Only 157 observations, which makes sense when you cross check to how many NAs there are in the Scientific name column of the main df:
```{r}
sum(is.na(alldata$Scientific_name))
```
157


## Export the unknown tag observations  and check in the IMOS database to see if we can ID any of them (conduct outside R)
```{r}
write_csv(unknown_tags, file = "../output/unknown_tags.csv")
#write_csv(unknown_tag_observations, file = "../output/unknown_tag_observations.csv")
```

## Notes:
Used the Mystery Tag tool in the IMOS database (https://animaltracking.aodn.org.au/tools/mysterytags)
All unknown tags unregistered apart from: 
A69-9001-3894 -> P. leopardus, tagged 2011 Heron Island
A69-9001-64693 -> Paul Butcher - Tiger
A69-9002-4128 -> Paul Butcher - White
A69-9002-8099 -> Heterodontus portusjacksoni tagged in 2013 in NSW (3 detections)
A69-9004-16367 -> new tag, registered but not yet deployed


* Quick dig into our dataset to see how many detections
```{r}
butcher_tags <- alldata %>% 
  filter(transmitter_id  %in%  c("A69-9001-64693", "A69-9002-4128"))
#write_csv(x = mystery, file = '../output/mystery.csv')
```




