---
title: "Data analysis and visualisation - big movers"
author: "Ben Cresswell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
 html_document:
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 4
    fig_width: 4
    highlight: textmate
    theme: spacelab
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: inline
---
# Created 17 May 2022 BJC
# Last edit 14 Jun 2022 BJC

#This document is designed to generate map of whole CSMP and then plot on the organisms that make big moves between these

# Set up Rmd
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load required packages
```{r packages, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(writexl)
library(readxl)
library(lubridate)
library(magrittr)
library(tidyverse)
#library(VTrack) # Current R version doesn't like VTrack - may need to install an earlier version..
```

# Load data
```{r}
#rm(list=ls())
load(file = "../data/RData/alldata.RData")
```

# Checks
```{r}
glimpse(alldata)
```

# Check locations etc
```{r}
alldata %>% 
  dplyr::select(project_name, site_code, installation_name, station_name, station_name_long, Location, Site, station_latitude, station_longitude, Lat, Long) %>% 
  distinct()

summary(alldata$Site) %>% 
  as.data.frame()
```

Location, Site, Lat, Long -> These are all information on tagging location which is why there are some missing values for these (some of these animals weren't tagged by us). (*Should probably go back through whole wrangling script and make this clear*)


# Filter out just the organisms we are interested in (the big movers!)
NB: we know these tag IDs from the EDA (abacus plots and unknown tags)
```{r filter-movers}
movers <- alldata %>% 
  filter(transmitter_id %in% c("A69-9001-64103", 
                             "A69-9001-60580", 
                             "A69-9001-64080", 
                             "A69-9001-63847", 
                             "A69-9001-4172",
                             "A69-9001-63947")) %>% 
  droplevels() %>% 
  mutate(transmitter_id = fct_relevel(transmitter_id, "A69-9001-64103", after = Inf)) %>%  # Have to move this individual to the end so their osprey obs doesn't overlap with 64080
  mutate(shark_id = factor(case_when(grepl('4172', transmitter_id) ~ 'Tiger 1',           # Create meaningful ID for later on
                                     grepl('63847', transmitter_id) ~ 'Tiger 2',
                                     grepl('63947', transmitter_id) ~ 'Tiger 3',
                                     grepl('64080', transmitter_id) ~ 'Silver 1',
                                     grepl('60580', transmitter_id) ~ 'Silver 2',
                                     grepl('64103', transmitter_id) ~ 'Grey 1'))) %>% 
  mutate(sharkloc = factor(case_when(grepl('4172', transmitter_id) ~ 'Tiger 1 - Saunders Reef',           # Create meaningful ID for later on
                                     grepl('63847', transmitter_id) ~ 'Tiger 3 - Cap. Bunkers',
                                     grepl('63947', transmitter_id) ~ 'Tiger 2 - Orpheus Island',
                                     grepl('64080', transmitter_id) ~ 'Silver 1 - Holmes Reef',
                                     grepl('60580', transmitter_id) ~ 'Grey 2 - Flinders Reef',
                                     grepl('64103', transmitter_id) ~ 'Grey 1 - Osprey Reef')))
  
```








# Check we've got the right ones in there
```{r check-id-filter}
# Simultaneously can check how many obs of each
movers %$% 
  summary(transmitter_id) 
movers %$% 
  summary(shark_id)
```

## So that's the main database imported. Will just need to insert 2 extra components to this:
1. Any detections external to our array (in this case only relevant for the GRS that turned up at Saunders Reef - 64103):

```{r}
ext_dets <- read_excel('../data/outside_array_fromAB.xlsx', trim_ws = TRUE) %>% 
transmute(transmitter_id = factor(paste(`code space`, ID, sep = '-')),      # Going to make this the same structure as the tag_locs object below..
         Scientific_name = factor(Scientific_name),
         Location = factor(location),
         Site = factor(Site),
         Lat = lat,
         Long = long,
         Date = as.Date(date, format = "%d.%m.%Y")) %>% 
mutate(shark_id = factor(case_when(grepl('4172', transmitter_id) ~ 'Tiger 1',           # Create meaningful ID for later on
                              grepl('63847', transmitter_id) ~ 'Tiger 2',
                              grepl('63947', transmitter_id) ~ 'Tiger 3',
                              grepl('64080', transmitter_id) ~ 'Silver 1',
                              grepl('60580', transmitter_id) ~ 'Silver 2',
                              grepl('64103', transmitter_id) ~ 'Grey 1'))) %>% 
  mutate(sharkloc = factor(case_when(grepl('4172', transmitter_id) ~ 'Tiger 1 - Saunders Reef',           # Create meaningful ID for later on
                                     grepl('63847', transmitter_id) ~ 'Tiger 3 - Cap. Bunkers',
                                     grepl('63947', transmitter_id) ~ 'Tiger 2 - Orpheus Island',
                                     grepl('64080', transmitter_id) ~ 'Silver 1 - Holmes Reef',
                                     grepl('60580', transmitter_id) ~ 'Grey 2 - Flinders Reef',
                                     grepl('64103', transmitter_id) ~ 'Grey 1 - Osprey Reef')))
ext_dets 
```

2. Original tagging/release locations - this information is actually already in the df, but we need to line it up with the detection information so we'll extract and then bind back

# Make df with original tagging locations in
```{r}
tag_locs <- movers %>% 
  dplyr::select(transmitter_id, Scientific_name, shark_id, sharkloc, Location, Site, Lat, Long, Date) %>% 
  distinct()
 
  tag_locs
```


# These 2 dfs are quite different to the main movers format but need to get them together if we want to graph together on the same plot
Need to mutate movers to be the same stx as tag_locs/ext_dets and bind them together.
```{r}
movers <- 
  movers %>% 
  mutate(transmitter_id = transmitter_id,
         Scientific_name = Scientific_name,
         shark_id = shark_id,
         sharkloc = sharkloc,
         Location = installation_name,
         Site = station_name,
         Lat = station_latitude,
         Long = station_longitude,
         Date = as.Date(detection_timestamp, format = "%d.%m.%Y"),
        .keep ='none') %>% 
  bind_rows(tag_locs, ext_dets) %>% 
  arrange(transmitter_id, Date)                                     # Need to make sure all detections are ordered by individual and also by date of detection
movers

```

## For Flinders and Holmes Reefs we make a distinction between N/S, E/W so we'll put in a variable that handles that.
We'll call it "sublocation". Obviously, the other reefs/locations won't have this, so we'll coalesce the location values over to that variable to avoid having NAs. Doesn't really matter either way..
```{r}
movers <- 
  movers %>% 
  mutate(Sublocation = factor(case_when(grepl("F1|F2|F3", Site) ~ 'Flinders - South',
                                 grepl("F4|F5|F6", Site) ~ 'Flinders - North',
                                 grepl("H1|H2", Site) ~ 'Holmes - West',
                                 grepl("H3|H4", Site) ~ 'Holmes - East'))) %>%  
  mutate(Sublocation = coalesce(Sublocation, Location))
```

Now we need to convert this 'raw' df into something we can use for plotting movement...

# 1. Movement by overall location
## We first need a df which just records when an animal moves reef (Location), ignoring small scale movements within that reef (i.e. by Site or Sublocation)
### The following chunk does this:
- 'Compresses' data so that multiple consecutive days observed at the same reef ('Location') are compressed into one observation -> need to do this to make geom_curve work
- We lose the 'Site' level information as we don't need it here (Note we do need this information to run the whole approach again at a finer resolution, but see below for the create of mover_sum_site) 
- We 'widen' the data by turning the Location column into separate To_Location and From_Location (and sub-location for checking) variables
```{r}
mover_sum_location <- 
  movers %>% 
  group_by(transmitter_id) %>%                                                     # Create a blank row per change in id. W/out this the  new 'to/from' vars will be mixed up across individuals
  group_modify(~ add_row(.x, .before=0)) %>%                                       # Put the row before each new transmitter_id. If you want it after then specify: group_modify(~ add_row(.x, .after = Inf))
  mutate(To_Location = lead(Location), .after = Location) %>%                      # Start creating to/from vars -> first for the locations (NB could do other way round using 'lag' instead of 'lead')
  rename(From_Location = Location) %>%                                             # 
  rename(From_Sublocation = Sublocation) %>%                                       # And for sublocations
  mutate(To_Sublocation = lead(From_Sublocation), .after = From_Sublocation) %>%   # 
  mutate(From_Lat = Lat,                                                           # And for lats/longs 
         From_Long = Long, .keep = "unused") %>%                                   #
  mutate(To_Lat = lead(From_Lat), .after = From_Lat) %>%                           #     
  mutate(To_Long = lead(From_Long), .after = From_Long) %>%                        # 
  mutate(From_Site = Site, .after = To_Sublocation,                                # And for sites
           To_Site = lead(From_Site), .keep = "unused") %>%                        # 
  filter(!is.na(From_Location),                                                    # Get rid of lines with NAs in the From column (these will basically be the line before the tagging event so obviously can't know this)
         !is.na(To_Location)) %>%                                                  # ..plus the one after the final entry for each animal (we don't know this either)
  filter(From_Sublocation != To_Sublocation,                                       # Finally, remove entries if the to/from sublocations or overall locations are the same (means no blue-water/large movement)
         From_Location != To_Location)                                         # Have to do both of these due to mismatch in names for tagging vs receiver locs
 
head(mover_sum_location)
```


# 1.a. We can now use this df to plot movements (see mapping_bigmovers) HOWEVER, where individuals have made the same movement the geom_curves will be stacked on top of each other obscuring all but one. SO..
## One option is to split this df up further for plotting -> into tigers and carcharhinids (so that arrows don't override each other)
```{r}
tiger_locmovs <- mover_sum_location %>% 
  filter(str_detect(Scientific_name, 'Galeo'))

other_locmovs <- mover_sum_location %>% 
  filter(str_detect(Scientific_name, 'Carch'))
```


# 2. Movement including sublocation moves -> this is for the zoomed in map 
This is similar to the above chunk but now includes sublocation movements (ie between Flin/Holm N/S/E/W). ∆ Note this uses the filter at the END to make sure there aren't any duplicate Sites (as opposed to the cumsum approach earlier)
```{r}
mover_sum_sublocation <- 
  movers %>% 
  group_by(transmitter_id) %>%                                                     # Create a blank row per change in id. W/out this the  new 'to/from' vars will be mixed up across individuals
  group_modify(~ add_row(.x, .before=0)) %>%                                       # Put the row before each new transmitter_id. If you want it after then specify: group_modify(~ add_row(.x, .after = Inf))
  mutate(To_Location = lead(Location), .after = Location) %>%                      # Start creating to/from vars -> first for the locations (NB could do other way round using 'lag' instead of 'lead')
  rename(From_Location = Location) %>%                                             # 
  rename(From_Sublocation = Sublocation) %>%                                       # And for sublocations
  mutate(To_Sublocation = lead(From_Sublocation), .after = From_Sublocation) %>%   # 
  mutate(From_Lat = Lat,                                                           # And for lats/longs 
         From_Long = Long, .keep = "unused") %>%                                   #
  mutate(To_Lat = lead(From_Lat), .after = From_Lat) %>%                           #     
  mutate(To_Long = lead(From_Long), .after = From_Long) %>%                        # 
  mutate(From_Site = Site, .after = To_Sublocation,                                # And for sites
           To_Site = lead(From_Site), .keep = "unused") %>%                        # 
  filter(!is.na(From_Location),                                                    # Get rid of lines with NAs in the From column (these will basically be the line before the tagging event so obviously can't know this)
         !is.na(To_Location)) %>%                                                  # ..plus the one after the final entry for each animal (we don't know this either)
  filter(From_Sublocation != To_Sublocation)                                       # Finally, remove entries if the to/from sublocations are the same (means no blue-water movement)

(mover_sum_sublocation)
```


## Can check diff between 2 dfs by looking at one individual
```{r}
mover_sum_location %>% 
  filter(transmitter_id == 'A69-9001-60580')

mover_sum_sublocation %>% 
  filter(transmitter_id == 'A69-9001-60580')

#check <- movers %>%   filter(transmitter_id == 'A69-9001-60580')
```

# 2.a. Will also split this up into tigers and carcharhinids (so that arrows don't override each other)
```{r}
tiger_sublocmovs <- mover_sum_sublocation %>% 
  filter(str_detect(Scientific_name, 'Galeo'))

other_sublocmovs <- mover_sum_sublocation %>% 
  filter(str_detect(Scientific_name, 'Carch'))
```

# Finally, split out tagging data - tigers vs others
```{r}
tag_locs_tigers <-
  tag_locs %>% 
  filter(Scientific_name == "Galeocerdo cuvier")

tag_locs_others <- 
  tag_locs %>% 
  filter(Scientific_name != "Galeocerdo cuvier")
```



######

