---
title: "Analysing residency indices"
aauthor: "Ben Cresswell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
 html_document:
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 4
    fig_width: 4
    highlight: textmate
    theme: spacelab
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: inline
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#rm(list=ls())
```


# Load required packages
```{r packages, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(sp)
library(rgdal)
library(rgeos)
library(adehabitatHR)
library(leaflet)
library(ggmap)    # for fortifying shapefiles
library(readxl)
library(scatterpie)
library(collapse)
library(tidyverse)
```



# Residency index

The residency index is the number of days an animal was detected within the receiver array (site residency) or tagging reef (reef residency) divided by the number of days monitored (i.e. number of days from the tagging date to the date of receiver retrieval) (Papastamatiou et al. 2010; Espinoza et al. 2011).



Prob need to start with alldata and wrangle out # of days at large vs detected...

The column 'Date' in alldata is the date the animal was tagged
Then there are 2 dates for receiver retrieval and we are going to want to figure out days at large from the later one of these..


```{r}
glimpse(alldata)
```









```{r}
alldata %>% 
  mutate(receiver_days = as.double(recoverydatetime_timestamp - deploymentdatetime_timestamp))
```



# Site residency - days spent at each site
```{r}
site_days <- alldata %>% 
  mutate(detection_date = as.Date(detection_timestamp)) %>%                     # Turn time stamp into date
  select(transmitter_id, detection_date, site_code, installation_name)# %>%      # Variables required
  select(!detection_date) %>% 
  #distinct() # %>% 
  group_by(transmitter_id, site_code) %>% 
  mutate(summarise(n = n()))

           
           
           
           
           
           
match(detection_date, sort(unique(detection_date))))
           
```

# Reef residency - days spent at each reef
```{r}
reef_days <- alldata %>% 
  mutate(detection_date = as.Date(detection_timestamp)) %>% 
  select(transmitter_id, detection_date, site_code, installation_name) %>% 
  group_by(transmitter_id, installation_name) %>% 
  mutate(reef_days = match(detection_date, sort(unique(detection_date)))) %>% 
  select(!c(detection_date, site_code)) %>% 
  distinct()

summary(reef_days$installation_name)
```

So now we have summaries of how many days these organisms were detected at both individual sites as well as reefs
Now we need to know how many days each organism was at large during the study period: the date of removal of the VR2W minus the date the animal was tagged.




```{r}

site_residence <- receivers %>% 
  select(site_code, rcvr_enddate) %>% 
  merge(site_days, by = 'site_code')
  
  
  
reef_residence <- receivers %>%   
  select(installation_name, rcvr_enddate) %>% 
  merge(reef_days, by = 'installation_name')



```







# Load receiver metadata again
```{r}
# Deployment 1
vr2ws_dep1 <- read_excel('../data/receiver_list_dep1.xlsx', trim_ws = TRUE) %>%
  tibble() %>% # Make into tibble format
  mutate_if(is.character, as.factor) # Sort out variables

# Deployment 2
vr2ws_dep2 <- read_excel('../data/receiver_list_dep2.xlsx', trim_ws = TRUE) %>%
  tibble() %>% # Make into tibble format
  mutate_if(is.character, as.factor) # Sort out variables
```

## Combine 
```{r}
receivers <- vr2ws_dep1 %>% 
  bind_rows(vr2ws_dep2) %>% 
  mutate(rcvr_enddate = ymd(recoverydatetime_timestamp)) %>%
  group_by(installation_name, site_code) %>% 
  filter(rcvr_enddate == max(rcvr_enddate))

```




```{r}


receiver_days <- alldata %>% 
    mutate(receiver_days = as.double(recoverydatetime_timestamp - deploymentdatetime_timestamp)) %>% 
  select(receiver_name, site_code, installation_name, receiver_days) %>% 
  distinct()
  
  
  
  
  group_by(installation_name, site_code) %>% 
  summarise(receiver_days = sum(receiver_days))
receiver_days
```





























